---
title: "prelim trajectories"
author: "An Bui"
date: "4/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source(here::here("code", "00-set_up.R"))

library(vegan)
library(patchwork)
```

# Tuesday 20 April 2021

## First pass

Going to try out the trajectories at Naples as a test first. The `percov` data frame is from `00-set_up.R` with some cleaning done over there.  

In this chunk, we're filtering out observations, calculating the mean percent cover per transect, and making things wider for putting into `metaMDS`. Each row in the data frame is a transect for one sampling date. Because it's a subset of the data, some species never show up at Naples; therefore, there's a bit of extra stuff to take out any species with 0 observations at the site. This probably isn't going to be an issue with the whole dataset.  

We're also making a metadata data frame, for plotting later. It has the sample ID, date, site, treatment, and the start/during/after categories.
```{r}
napl_traj_df <- percov %>% 
  # filter for Naples observations, algae only
  filter(site == "NAPL" & group == "algae") %>% 
  # calculate mean and sum percent cover across 4 quads (i.e. per transect)
  group_by(sample_ID, scientific_name) %>% 
  summarize(mean_pc = mean(percent_cover),
            sum_pc = sum(percent_cover)) %>% 
  ungroup() %>% 
  # filter out species with 0 observations
  filter(sum_pc > 0) %>% 
  select(-sum_pc) %>% 
  # get into wide form
  pivot_wider(names_from = "scientific_name", values_from = "mean_pc") %>% 
  # make the sample_ID column row names
  column_to_rownames("sample_ID") %>% 
  # replace NA with 0
  replace(is.na(.), 0)
  
napl_traj_meta <- percov %>% 
  # filter for Naples observations, algae only
  filter(site == "NAPL" & group == "algae") %>% 
  select(sample_ID, date, site, treatment, exp_dates) %>% 
  # only keep unique descriptors
  unique()
```

Going to try a few ordinations - presence/absence (Raup-Crick, appropriate for disentangling variation in composition from variation in alpha diversity) and abundance (Bray-Curtis, though I'm not sure this is the right metric because it's not raw count data. Blah!).

```{r}
napl_rc_dist <- vegdist(napl_traj_df, "raup")
napl_rc_MDS <- metaMDS(napl_rc_dist, "raup")

napl_bray_dist <- vegdist(napl_traj_df, "bray")
napl_bray <- metaMDS(napl_bray_dist)
```

Now, going to put the outputs into data frames to plot.

```{r}
napl_rc_plotdf <- scores(napl_rc_MDS, display = "sites") %>%
    as_tibble() %>% 
    bind_cols(napl_traj_meta, .)

napl_bray_plotdf <- scores(napl_bray, display = "sites") %>% 
  as_tibble() %>% 
  bind_cols(napl_traj_meta, .)

napl_rc_plot_contin <- ggplot(napl_rc_plotdf %>% filter(exp_dates %in% c("start", "after") & treatment == "CONTINUAL"), aes(x = NMDS1, y = NMDS2)) +
  coord_fixed() + 
  geom_segment(aes(xend = c(tail(NMDS1, n = -1), NA), 
                     yend = c(tail(NMDS2, n = -1), NA)),
                 arrow = arrow(length = unit(0.4, "cm"), type = "closed"),
                 size = 0.5, color = "grey") +
  geom_point(aes(color = exp_dates), size = 5) +
  scale_x_continuous(limits = c(-0.3, 0.37)) +
  scale_y_continuous(limits = c(-0.3, 0.4)) +
  theme(panel.background = element_rect("white"),
        panel.border = element_rect("grey85", fill = NA),
        legend.background = element_rect("white"),
        legend.position = "none") +
  labs(title = "Continual removal")
napl_rc_plot_contin

napl_rc_plot_annu <- ggplot(napl_rc_plotdf %>% filter(exp_dates %in% c("start", "after") & treatment == "ANNUAL"), aes(x = NMDS1, y = NMDS2)) +
  coord_fixed() + 
  geom_segment(aes(xend = c(tail(NMDS1, n = -1), NA), 
                     yend = c(tail(NMDS2, n = -1), NA)),
                 arrow = arrow(length = unit(0.4, "cm"), type = "closed"),
                 size = 0.5, color = "grey") +
  geom_point(aes(color = exp_dates), size = 5) +
  scale_x_continuous(limits = c(-0.3, 0.37)) +
  scale_y_continuous(limits = c(-0.3, 0.4)) +
  theme(panel.background = element_rect("white"),
        panel.border = element_rect("grey85", fill = NA),
        legend.background = element_rect("white"),
        legend.position = "bottom") +
  labs(title = "Annual removal")
napl_rc_plot_annu

napl_rc_plot_control <- ggplot(napl_rc_plotdf %>% filter(exp_dates %in% c("start", "after") & treatment == "CONTROL"), aes(x = NMDS1, y = NMDS2)) +
  coord_fixed() + 
  geom_segment(aes(xend = c(tail(NMDS1, n = -1), NA), 
                     yend = c(tail(NMDS2, n = -1), NA)),
                 arrow = arrow(length = unit(0.4, "cm"), type = "closed"),
                 size = 0.5, color = "grey") +
  geom_point(aes(color = exp_dates), size = 5) +
  scale_x_continuous(limits = c(-0.3, 0.37)) +
  scale_y_continuous(limits = c(-0.3, 0.4)) +
  theme(panel.background = element_rect("white"),
        panel.border = element_rect("grey85", fill = NA),
        legend.background = element_rect("white"),
        legend.position = "none") +
  labs(title = "Control")
napl_rc_plot_control

napl_rc_plot_grid <- napl_rc_plot_contin + napl_rc_plot_annu + napl_rc_plot_control

# ggsave(here::here("figures/trajectories/prelim-trajectories", "NAPL-traj-2021-04-20.jpg"), napl_rc_plot_grid, dpi = 200, height = 7, width = 15)
```

They are the same!!!!!! lolllll!!!  

Some permanova/betadisper stuff here. Had to filter out "after" observations, so there's a bunch of that.

```{r}
napl_after_df <- napl_traj_df %>% 
  rownames_to_column("sample_ID") %>% 
  filter(sample_ID %in% napl_after_sampleIDs) %>% 
  column_to_rownames("sample_ID")

napl_after_meta <- napl_traj_meta %>% 
  filter(sample_ID %in% napl_after_sampleIDs)

napl_traj_permanova_rc <- adonis(napl_after_df ~ treatment, napl_after_meta, method = "raup")

napl_traj_permanova_rc_df <- napl_traj_permanova_rc$aov.tab$Df[1]
napl_traj_permanova_rc_ss <- round(napl_traj_permanova_rc$aov.tab$SumsOfSqs[1], 2)
napl_traj_permanova_rc_fstat <- round(napl_traj_permanova_rc$aov.tab$F.Model[1], 2)
napl_traj_permanova_rc_p <- round(napl_traj_permanova_rc$aov.tab$'Pr(>F)'[1], 4)

napl_traj_permanova_caption <- paste("PerMANOVA, F(",
                                    napl_traj_permanova_rc_df, ", ",
                                    napl_traj_permanova_rc_ss, ") = ",
                                    napl_traj_permanova_rc_fstat, ", p = ",
                                    napl_traj_permanova_rc_p,
                                    sep = "")

# no significant difference in centroids between experiment dates

exp_dates_group <- napl_traj_meta %>% 
  select(sample_ID, exp_dates) %>% 
  deframe()

treatment_group <- napl_traj_meta %>% 
  select(sample_ID, treatment) %>% 
  deframe()

napl_rc_bd <- betadisper(napl_rc_dist, exp_dates_group)
anova(napl_rc_bd)
# significant difference in dispersion between experiment dates
```

# Wednesday 21 April 2021

Ok, well, yesterday was kind of a bummer. Still not 100% sure if I should be using Raup-Crick or Jaccard, so just gonna do the same thing except with Jaccard for Naples.

```{r}
# calculating jaccard distance matrix
napl_jacc_dist <- vegdist(napl_traj_df, "jaccard")

# doing NMDS
napl_jacc_MDS <- metaMDS(napl_rc_dist, "jaccard")

# extracting coordinates from jaccard MDS
napl_jacc_plotdf <- scores(napl_jacc_MDS, display = "sites") %>%
    as_tibble() %>% 
    bind_cols(napl_traj_meta, .)

# plotting
napl_jacc_plot_contin <- ggplot(napl_jacc_plotdf %>% filter(exp_dates %in% c("start", "after") & treatment == "CONTINUAL"), aes(x = NMDS1, y = NMDS2)) +
  coord_fixed() + 
  geom_segment(aes(xend = c(tail(NMDS1, n = -1), NA), 
                     yend = c(tail(NMDS2, n = -1), NA)),
                 arrow = arrow(length = unit(0.4, "cm"), type = "closed"),
                 size = 0.5, color = "grey") +
  geom_point(aes(color = exp_dates), size = 5) +
  scale_x_continuous(limits = c(-0.3, 0.37)) +
  scale_y_continuous(limits = c(-0.3, 0.4)) +
  theme(panel.background = element_rect("white"),
        panel.border = element_rect("grey85", fill = NA),
        legend.background = element_rect("white"),
        legend.position = "none") +
  labs(title = "Continual removal")
napl_jacc_plot_contin

napl_jacc_plot_annu <- ggplot(napl_jacc_plotdf %>% filter(exp_dates %in% c("start", "after") & treatment == "ANNUAL"), aes(x = NMDS1, y = NMDS2)) +
  coord_fixed() + 
  geom_segment(aes(xend = c(tail(NMDS1, n = -1), NA), 
                     yend = c(tail(NMDS2, n = -1), NA)),
                 arrow = arrow(length = unit(0.4, "cm"), type = "closed"),
                 size = 0.5, color = "grey") +
  geom_point(aes(color = exp_dates), size = 5) +
  scale_x_continuous(limits = c(-0.3, 0.37)) +
  scale_y_continuous(limits = c(-0.3, 0.4)) +
  theme(panel.background = element_rect("white"),
        panel.border = element_rect("grey85", fill = NA),
        legend.background = element_rect("white")) +
  labs(title = "Annual removal")
napl_jacc_plot_annu

napl_jacc_plot_contr <- ggplot(napl_jacc_plotdf %>% filter(exp_dates %in% c("start", "after") & treatment == "CONTROL"), aes(x = NMDS1, y = NMDS2)) +
  coord_fixed() + 
  geom_segment(aes(xend = c(tail(NMDS1, n = -1), NA), 
                     yend = c(tail(NMDS2, n = -1), NA)),
                 arrow = arrow(length = unit(0.4, "cm"), type = "closed"),
                 size = 0.5, color = "grey") +
  geom_point(aes(color = exp_dates), size = 5) +
  scale_x_continuous(limits = c(-0.3, 0.37)) +
  scale_y_continuous(limits = c(-0.3, 0.4)) +
  theme(panel.background = element_rect("white"),
        panel.border = element_rect("grey85", fill = NA),
        legend.background = element_rect("white"),
        legend.position = "none") +
  labs(title = "Control")
napl_jacc_plot_contr

jacc_plot_grid <- napl_jacc_plot_contin + napl_jacc_plot_annu + napl_jacc_plot_contr

# ggsave(here::here("figures/trajectories/prelim-trajectories", "NAPL-traj-jacc-2021-04-21.jpg"), jacc_plot_grid, dpi = 200, height = 7, width = 15)

```

Welp, they're the same.  

I know in my heart I should start looking at the biomass stuff but man I don't want to. So... I guess I'm going to look at all the sites instead lol. Sorry not sorry.

```{r}
traj_df <- percov %>% 
  # filter for algae only
  filter(group == "algae") %>% 
  # calculate mean and sum percent cover across 4 quads (i.e. per transect)
  group_by(sample_ID, scientific_name) %>% 
  summarize(mean_pc = mean(percent_cover),
            sum_pc = sum(percent_cover)) %>% 
  ungroup() %>% 
  # filter out species with 0 observations
  filter(sum_pc > 0) %>% 
  select(-sum_pc) %>% 
  # get into wide form
  pivot_wider(names_from = "scientific_name", values_from = "mean_pc") %>% 
  # make the sample_ID column row names
  column_to_rownames("sample_ID") %>% 
  # replace NA with 0
  replace(is.na(.), 0)

traj_meta <- percov %>% 
  # filter for algae only
  filter(group == "algae") %>% 
  select(sample_ID, date, site, treatment, exp_dates) %>% 
  unite("date_site", date, site, remove = FALSE) %>% 
  # only keep unique descriptors
  unique()
```

Now to try the ordinations again.

```{r}
rc_dist <- vegdist(traj_df, "raup")
rc_mds <- metaMDS(all_rc_dist, "raup")
```

And then prep to plot, and plotting.

```{r}
rc_plotdf <- scores(rc_mds, display = "sites") %>%
    as_tibble() %>% 
    bind_cols(traj_meta, .)

rc_plot_contin <- ggplot(rc_plotdf %>% filter(exp_dates %in% c("start", "after") & treatment == "CONTINUAL"), aes(x = NMDS1, y = NMDS2)) +
  coord_fixed() + 
  geom_segment(aes(xend = c(tail(NMDS1, n = -1), NA), 
                   yend = c(tail(NMDS2, n = -1), NA),
                   color = site),
               arrow = arrow(length = unit(0.3, "cm"), type = "closed"),
               size = 0.5) +
  scale_x_continuous(limits = c(-0.4, 0.5)) +
  scale_y_continuous(limits = c(-0.35, 0.23)) +
  theme(panel.background = element_rect("white"),
        panel.border = element_rect("grey85", fill = NA),
        legend.background = element_rect("white")) +
  labs(title = "Continual removal")
rc_plot_contin

rc_plot_annu <- ggplot(rc_plotdf %>% filter(exp_dates %in% c("start", "after") & treatment == "ANNUAL"), aes(x = NMDS1, y = NMDS2)) +
  coord_fixed() + 
  geom_segment(aes(xend = c(tail(NMDS1, n = -1), NA), 
                   yend = c(tail(NMDS2, n = -1), NA),
                   color = site),
               arrow = arrow(length = unit(0.3, "cm"), type = "closed"),
               size = 0.5) +
  scale_x_continuous(limits = c(-0.5, 0.5)) +
  scale_y_continuous(limits = c(-0.35, 0.3)) +
  theme(panel.background = element_rect("white"),
        panel.border = element_rect("grey85", fill = NA),
        legend.background = element_rect("white")) +
  labs(title = "Annual removal")
rc_plot_annu

rc_plot_contr <- ggplot(rc_plotdf %>% filter(exp_dates %in% c("start", "after") & treatment == "CONTROL"), aes(x = NMDS1, y = NMDS2)) +
  coord_fixed() + 
  geom_segment(aes(xend = c(tail(NMDS1, n = -1), NA), 
                   yend = c(tail(NMDS2, n = -1), NA),
                   color = site),
               arrow = arrow(length = unit(0.3, "cm"), type = "closed"),
               size = 0.5) +
  scale_x_continuous(limits = c(-0.5, 0.5)) +
  scale_y_continuous(limits = c(-0.35, 0.3)) +
  theme(panel.background = element_rect("white"),
        panel.border = element_rect("grey85", fill = NA),
        legend.background = element_rect("white")) +
  labs(title = "Control")
rc_plot_contr
```

Ok, I messed around with this but idk what I'm actually doing lol. Part of the issue is that I'm not sure if I need to change the `exp_date` thing around so that "start" isn't in its own group. Going to think more on this tomorrow...

```{r}
rc_traj_permanova <- adonis(traj_df ~ treatment*date_site, traj_meta, method = "raup")

rc_traj_permanova_df <- rc_traj_permanova$aov.tab$Df[1]
rc_traj_permanova_ss <- round(rc_traj_permanova$aov.tab$SumsOfSqs[1], 2)
rc_traj_permanova_fstat <- round(rc_traj_permanova$aov.tab$F.Model[1], 2)
rc_traj_permanova_p <- round(rc_traj_permanova$aov.tab$'Pr(>F)'[1], 4)

rc_traj_permanova_caption <- paste("PerMANOVA, F(",
                                    rc_traj_permanova_df, ", ",
                                    rc_traj_permanova_ss, ") = ",
                                    rc_traj_permanova_fstat, ", p = ",
                                    rc_traj_permanova_p,
                                    sep = "")

exp_dates_all <- traj_meta %>% 
  select(sample_ID, date_site) %>% 
  deframe()

rc_traj_bd <- betadisper(rc_dist, exp_dates_all)
anova(rc_traj_bd)
```
Output of `adonis` function:  

Call:  
adonis(formula = traj_df ~ treatment * exp_dates, data = traj_meta,      method = "raup")   

Permutation: free  
Number of permutations: 999  

Terms added sequentially (first to last)  

                     Df SumsOfSqs   MeanSqs F.Model       R2 Pr(>F)    
treatment             2    0.0579  0.028942  0.8859  0.00215  0.501  
exp_dates             2    0.4422  0.221088  6.7679  0.01642  0.028 *
treatment:exp_dates   4   -0.0044 -0.001103 -0.0338 -0.00016  0.698  
Residuals           809   26.4278  0.032667          0.98159         
Total               817   26.9234                    1.00000         
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Results from ANOVA of dispersion:
Analysis of Variance Table  

Response: Distances  
           Df  Sum Sq Mean Sq F value    Pr(>F)     
Groups      2  1.2899 0.64497  35.491 1.664e-15 ***
Residuals 815 14.8109 0.01817                      
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Not sure this is right because the "start" category only has one community. 

# Monday 31 May 2021

Hello darkness my old friend. Ok, so trying to make those trajectory plots, but now with:  
  1) continual and annual removal plotted on top of each other,  
  2) control plots without trajectory but just grey circles (???) 
  
So this is the attempt for that, for Naples with Jaccard. Doing the NMDS again because I just want the after dates.
  
```{r}
napl_jacc_after <- metaMDS(napl_after_df, "jacc")

# extracting coordinates from jaccard MDS
napl_jacc_plotdf <- scores(napl_jacc_MDS, display = "sites") %>%
    as_tibble() %>% 
    bind_cols(napl_traj_meta, .)

all_napl_jacc <- scores(napl_jacc_after, display = "sites") %>% 
  as_tibble() %>% 
  bind_cols(napl_after_meta, .)

napl_jacc_plot_all <- ggplot() +
  coord_fixed() + 
  # continual
  geom_segment(data = all_napl_jacc %>% filter(treatment == "CONTINUAL"), 
               aes(x = NMDS1, y = NMDS2, 
                   xend = c(tail(NMDS1, n = -1), NA), 
                   yend = c(tail(NMDS2, n = -1), NA)),
               arrow = arrow(length = unit(0.3, "cm"), type = "closed"),
               size = 0.4, color = "grey", alpha = 0.9) +
  geom_point(data = all_napl_jacc %>% filter(treatment == "CONTINUAL"),
             aes(x = NMDS1, y = NMDS2, 
                 color = "Continual removal", shape = "Continual removal"), 
             size = 4) +
  
  # annual
  geom_segment(data = all_napl_jacc %>% filter(treatment == "ANNUAL"), 
               aes(x = NMDS1, y = NMDS2, 
                   xend = c(tail(NMDS1, n = -1), NA), 
                   yend = c(tail(NMDS2, n = -1), NA)),
               arrow = arrow(length = unit(0.3, "cm"), type = "closed"),
               size = 0.4, color = "grey", alpha = 0.9) +
  geom_point(data = all_napl_jacc %>% filter(treatment == "ANNUAL"),
             aes(x = NMDS1, y = NMDS2, 
                 color = "Annual removal", shape = "Annual removal"), size = 4) +
  
  # control
  geom_point(data = all_napl_jacc %>% filter(treatment == "CONTROL"),
             aes(x = NMDS1, y = NMDS2, 
                 color = "Control", shape = "Control"), size = 3, alpha = 0.5) +
  
  # legend
  scale_color_manual(name = NULL,
                     breaks = c("Annual removal", "Continual removal", "Control"),
                     values = c("Annual removal" = annual_col,
                                "Continual removal" = continual_col,
                                "Control" = "#000000")) +
  scale_shape_manual(name = NULL,
                     breaks = c("Annual removal", "Continual removal", "Control"),
                     values = c("Annual removal" = annual_shape,
                                "Continual removal" = continual_shape,
                                "Control" = 21)) +
  
  # scale_x_continuous(limits = c(-0.3, 0.37)) +
  # scale_y_continuous(limits = c(-0.3, 0.4)) +
  theme(panel.background = element_rect("white"),
        panel.border = element_rect("grey85", fill = NA),
        legend.background = element_rect("white")) +
  labs(title = "NAPL")
napl_jacc_plot_all
```

Doing with all sites now.
```{r}
all_traj_df <- percov %>% 
  # filter for algae only
  filter(group == "algae") %>% 
  # calculate mean and sum percent cover across 4 quads (i.e. per transect)
  group_by(sample_ID, scientific_name) %>% 
  summarize(mean_pc = mean(percent_cover),
            sum_pc = sum(percent_cover)) %>% 
  ungroup() %>% 
  # filter out species with 0 observations
  filter(sum_pc > 0) %>% 
  select(-sum_pc) %>% 
  # get into wide form
  pivot_wider(names_from = "scientific_name", values_from = "mean_pc") %>% 
  # make the sample_ID column row names
  column_to_rownames("sample_ID") %>% 
  # replace NA with 0
  replace(is.na(.), 0)

all_traj_meta <- percov %>% 
  # filter for algae only
  filter(group == "algae") %>% 
  select(sample_ID, date, site, treatment, exp_dates) %>% 
  # only keep unique descriptors
  unique()

all_after_df <- all_traj_df %>% 
  rownames_to_column("sample_ID") %>% 
  filter(sample_ID %in% all_after_sampleIDs) %>% 
  column_to_rownames("sample_ID")

all_after_meta <- all_traj_meta %>% 
  filter(sample_ID %in% all_after_sampleIDs)

all_jacc_MDS <- metaMDS(all_after_df, "jacc")

# extracting coordinates from jaccard MDS
all_jacc_plotdf <- scores(all_jacc_MDS, display = "sites") %>%
    as_tibble() %>% 
    bind_cols(all_after_meta, .)

all_jacc_plot <- ggplot() +
  coord_fixed() + 
  # continual
  geom_segment(data = all_jacc_plotdf %>% filter(treatment == "CONTINUAL"), 
               aes(x = NMDS1, y = NMDS2, 
                   xend = c(tail(NMDS1, n = -1), NA), 
                   yend = c(tail(NMDS2, n = -1), NA)),
               arrow = arrow(length = unit(0.3, "cm"), type = "closed"),
               size = 0.4, color = "grey", alpha = 0.9) +
  geom_point(data = all_jacc_plotdf %>% filter(treatment == "CONTINUAL"),
             aes(x = NMDS1, y = NMDS2, 
                 color = "Continual removal", shape = "Continual removal"), 
             size = 3) +
  
  # annual
  geom_segment(data = all_jacc_plotdf %>% filter(treatment == "ANNUAL"), 
               aes(x = NMDS1, y = NMDS2, 
                   xend = c(tail(NMDS1, n = -1), NA), 
                   yend = c(tail(NMDS2, n = -1), NA)),
               arrow = arrow(length = unit(0.3, "cm"), type = "closed"),
               size = 0.4, color = "grey", alpha = 0.9) +
  geom_point(data = all_jacc_plotdf %>% filter(treatment == "ANNUAL"),
             aes(x = NMDS1, y = NMDS2, 
                 color = "Annual removal", shape = "Annual removal"), size = 3) +
  
  # control
  geom_point(data = all_jacc_plotdf %>% filter(treatment == "CONTROL"),
             aes(x = NMDS1, y = NMDS2, 
                 color = "Control", shape = "Control"), size = 2, alpha = 0.5) +
  
  # legend
  scale_color_manual(name = NULL,
                     breaks = c("Annual removal", "Continual removal", "Control"),
                     values = c("Annual removal" = annual_col,
                                "Continual removal" = continual_col,
                                "Control" = "#000000")) +
  scale_shape_manual(name = NULL,
                     breaks = c("Annual removal", "Continual removal", "Control"),
                     values = c("Annual removal" = annual_shape,
                                "Continual removal" = continual_shape,
                                "Control" = 21)) +
  
  scale_x_continuous(limits = c(-1.1, 1.75)) +
  scale_y_continuous(limits = c(-1.1, 1.2)) +
  theme(panel.background = element_rect("white"),
        panel.border = element_rect("grey85", fill = NA),
        strip.background = element_rect("white"),
        strip.text = element_text(hjust = 0, size = 13), 
        legend.background = element_rect("white"),
        legend.position = "bottom") +
  facet_wrap(~site, nrow = 2)
all_jacc_plot
ggsave(here::here("figures", "traj.jpg"), all_jacc_plot, width = 8, height = 6, dpi = 200)

all_plot_fxn <- function(site_choice) {
  ggplot() +
    coord_fixed() + 
    # continual
    geom_segment(data = all_jacc_plotdf %>% filter(site == site_choice & treatment == "CONTINUAL"), 
                 aes(x = NMDS1, y = NMDS2, 
                     xend = c(tail(NMDS1, n = -1), NA), 
                     yend = c(tail(NMDS2, n = -1), NA)),
                 arrow = arrow(length = unit(0.3, "cm")),
                 size = 0.4, color = "grey", alpha = 0.9) +
    geom_point(data = all_jacc_plotdf %>% filter(site == site_choice & treatment == "CONTINUAL"),
               aes(x = NMDS1, y = NMDS2, 
                   color = "Continual removal", shape = "Continual removal"), 
               size = 4) +
    
    # annual
    geom_segment(data = all_jacc_plotdf %>% filter(site == site_choice & treatment == "ANNUAL"), 
                 aes(x = NMDS1, y = NMDS2, 
                     xend = c(tail(NMDS1, n = -1), NA), 
                     yend = c(tail(NMDS2, n = -1), NA)),
                 arrow = arrow(length = unit(0.3, "cm")),
                 size = 0.4, color = "grey", alpha = 0.9) +
    geom_point(data = all_jacc_plotdf %>% filter(site == site_choice & treatment == "ANNUAL"),
               aes(x = NMDS1, y = NMDS2, 
                   color = "Annual removal", shape = "Annual removal"), size = 4) +
    
    # control
    geom_point(data = all_jacc_plotdf %>% filter(site == site_choice & treatment == "CONTROL"),
               aes(x = NMDS1, y = NMDS2, 
                   color = "Control", shape = "Control"), size = 3, alpha = 0.5) +
    
    # legend
    scale_color_manual(name = NULL,
                       breaks = c("Annual removal", "Continual removal", "Control"),
                       values = c("Annual removal" = annual_col,
                                  "Continual removal" = continual_col,
                                  "Control" = "#000000")) +
    scale_shape_manual(name = NULL,
                       breaks = c("Annual removal", "Continual removal", "Control"),
                       values = c("Annual removal" = annual_shape,
                                  "Continual removal" = continual_shape,
                                  "Control" = 21)) +
    
    scale_x_continuous(limits = c(-1.1, 1.75)) +
    scale_y_continuous(limits = c(-1.1, 1.2)) +
    theme(panel.background = element_rect("white"),
          panel.border = element_rect("grey85", fill = NA),
          legend.background = element_rect("white")) +
    labs(title = site_choice)
}

aque_plot <- all_plot_fxn("AQUE") + theme(legend.position = "none")
carp_plot <- all_plot_fxn("CARP") + theme(legend.position = "bottom")
mohk_plot <- all_plot_fxn("MOHK") + theme(legend.position = "none")
ivee_plot <-   ggplot() +
    coord_fixed() + 
    # annual
    geom_segment(data = all_jacc_plotdf %>% filter(site == "IVEE" & treatment == "ANNUAL"), 
                 aes(x = NMDS1, y = NMDS2, 
                     xend = c(tail(NMDS1, n = -1), NA), 
                     yend = c(tail(NMDS2, n = -1), NA)),
                 arrow = arrow(length = unit(0.3, "cm")),
                 size = 0.4, color = "grey", alpha = 0.9) +
    geom_point(data = all_jacc_plotdf %>% filter(site == "IVEE" & treatment == "ANNUAL"),
               aes(x = NMDS1, y = NMDS2, 
                   color = "Annual removal", shape = "Annual removal"), size = 4) +
    
    # control
    geom_point(data = all_jacc_plotdf %>% filter(site == "IVEE" & treatment == "CONTROL"),
               aes(x = NMDS1, y = NMDS2, 
                   color = "Control", shape = "Control"), size = 3, alpha = 0.5) +
    
    # legend
    scale_color_manual(name = NULL,
                       breaks = c("Annual removal", "Control"),
                       values = c("Annual removal" = annual_col,
                                  "Control" = "#000000")) +
    scale_shape_manual(name = NULL,
                       breaks = c("Annual removal", "Control"),
                       values = c("Annual removal" = annual_shape,
                                  "Control" = 21)) +
    
    scale_x_continuous(limits = c(-1.1, 1.75)) +
    scale_y_continuous(limits = c(-1.1, 1.2)) +
    theme(panel.background = element_rect("white"),
          panel.border = element_rect("grey85", fill = NA),
          legend.position = "none") +
    labs(title = "IVEE")
napl_plot <- all_plot_fxn("NAPL") + theme(legend.position = "none")

plots_together <- (aque_plot + mohk_plot + napl_plot) / 
                  (ivee_plot + carp_plot + plot_spacer()) +
  plot_layout(nrow = 2, widths = c(1, 1, 1, 1, 1, 1), heights = c(1, 1, 1, 1, 1, 1)) 
plots_together
ggsave(here::here("figures", "traj.jpg"), plots_together, width = 8, height = 6, dpi = 200)
```

```{r}
all_traj_permanova_jacc <- adonis(all_after_df ~ treatment, all_after_meta, method = "jacc")

all_traj_permanova_jacc_df <- all_traj_permanova_jacc$aov.tab$Df[1]
all_traj_permanova_jacc_ss <- round(all_traj_permanova_jacc$aov.tab$SumsOfSqs[1], 2)
all_traj_permanova_jacc_fstat <- round(all_traj_permanova_jacc$aov.tab$F.Model[1], 2)
all_traj_permanova_jacc_p <- round(all_traj_permanova_jacc$aov.tab$'Pr(>F)'[1], 4)

all_traj_permanova_caption <- paste("PerMANOVA, F(",
                                    all_traj_permanova_jacc_df, ", ",
                                    all_traj_permanova_jacc_ss, ") = ",
                                    all_traj_permanova_jacc_fstat, ", p = ",
                                    all_traj_permanova_jacc_p,
                                    sep = "")

# no significant difference in centroids between experiment dates

# pairwise posthoc test for adonis
library(pairwiseAdonis)
pair.mod <- pairwise.adonis(all_after_df,
                            all_after_meta$treatment,
                            sim.method = "jacc")

treatment_group <- all_traj_meta %>% 
  select(sample_ID, treatment) %>% 
  deframe()

all_jacc_dist <- vegdist(all_after_df, "jacc")
all_jacc_bd <- betadisper(all_jacc_dist, treatment_group)
anova(jacc_jacc_bd)
# significant difference in dispersion between experiment dates
```





