---
title: "kelp frond recovery"
author: "An Bui"
date: "1/23/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 0. set up
```{r}
source(here::here("code", "00-set_up.R"))
```

# 1. Kelp biomass

## Data frames

`kelp_fronds` is created in the set up script - each row is a part of a transect with a unique `sample_ID`. Observations with `-99999` have also been filtered out.

## More wrangling

Data frames:  
- `delta_fronds`: calculates difference in frond density between control and removal plots (removal - control)  
- `control_fronds`: kelp fronds from control plots only  
- `total_fronds`: kelp fronds from treatment + control plots
- `delta_biomass`: calculates difference in biomass between control and removal plots (removal - control)  
- `kelp_biomass`: biomass from treatment + control plots

```{r}
# total fronds
total_fronds <- kelp_fronds %>% 
  group_by(site, year, month, treatment, date) %>% 
  summarize(total_fronds = sum(fronds)) %>% 
  ungroup() %>% 
  # # make a new column for after dates
  # after_dates_column() %>% 
  # make a new column for during and after and set factor levels
  exp_dates_column() %>% 
  # create a new column for season and set factor levels
  season_column() %>% 
  filter(total_fronds > -1) 

# delta fronds
delta_fronds <- total_fronds %>% 
  pivot_wider(names_from = treatment, values_from = total_fronds) %>% 
  mutate(delta_annual = annual - control,
         delta_continual = continual - control) 

# just control
control_fronds <- total_fronds %>% 
  filter(treatment == "control")

# total biomass
kelp_biomass <- biomass %>% 
  filter(sp_code == "MAPY") %>% 
  dplyr::select(-sp_code) %>% 
  # # make a new column for after dates
  after_dates_column() %>% 
  # make a new column for during and after and set factor levels
  exp_dates_column()
  # select(site, year, month, treatment, date, wm_gm2)

# delta biomass
delta_biomass <- kelp_biomass %>% 
  dplyr::select(site, year, month, treatment, date, exp_dates, dry_gm2) %>% 
  pivot_wider(names_from = treatment, values_from = dry_gm2) %>% 
  mutate(delta_annual = annual - control,
         delta_continual = continual - control) 
```

Also as of 2022-03-07, finally admitting to myself that there needs to be separate data frames for annual and continual.

```{r}
delta_annual <- delta_biomass %>% 
  dplyr::select(site, year, month, date, control, annual, delta_annual) %>% 
  drop_na(delta_annual) %>% 
  mutate(exp_dates = case_when(
    # after for annual removal:
    site == "aque" & date >= aque_after_date_annual ~ "after",
    site == "napl" & date >= napl_after_date_annual ~ "after",
    site == "ivee" & date >= ivee_after_date_annual ~ "after",
    site == "mohk" & date >= mohk_after_date_annual ~ "after",
    site == "carp" & date >= carp_after_date_annual ~ "after",
    # everything else is "during" the experiment
    TRUE ~ "during"
  ),
  exp_dates = fct_relevel(exp_dates, c("during", "after"))) %>% 
   # create a column for quarter
  mutate(quarter = case_when(
    month <= 3 ~ "Q1",
    month <= 6 ~ "Q2",
    month <= 9 ~ "Q3",
    TRUE ~ "Q4"
  )) %>% 
  # calculate time since start of experiment
  mutate(time_yrs = case_when(
    # AQUE, NAPL, MOHK, CARP: control and annual started in 2008
    site %in% c("aque", "napl", "mohk", "carp") & quarter == "Q1" ~ year + 0.125 - 2008,
    site %in% c("aque", "napl", "mohk", "carp") & quarter == "Q2" ~ year + 0.375 - 2008,
    site %in% c("aque", "napl", "mohk", "carp") & quarter == "Q3" ~ year + 0.625 - 2008,
    site %in% c("aque", "napl", "mohk", "carp") & quarter == "Q4" ~ year + 0.875 - 2008, 
    # IVEE control and annual started in 2011
    site == "ivee" & quarter == "Q1" ~ year + 0.125 - 2011,
    site == "ivee" & quarter == "Q2" ~ year + 0.375 - 2011,
    site == "ivee" & quarter == "Q3" ~ year + 0.625 - 2011,
    site == "ivee" & quarter == "Q4" ~ year + 0.875 - 2011
    )) %>% 
  group_by(site) %>% 
  mutate(time_since_start = time_yrs - min(time_yrs)) %>% 
  ungroup() %>% 
  # calculate time since end of experiment
  group_by(site, exp_dates) %>% 
  # if "after", then simple: the time in years - the minimum time in years
  # if "during", then more complex: take the max time in years and add 0.25, then subtract the time in years
  mutate(time_since_end = case_when(
    exp_dates == "during" ~ -(max(time_yrs) + 0.25 - time_yrs),
    exp_dates == "after" ~ time_yrs - min(time_yrs)
  )) %>% 
  ungroup() %>% 
  left_join(., enframe(sites_full), by = c("site" = "name")) %>% 
  rename(site_full = value) %>% 
  mutate(site_full = fct_relevel(site_full, "Arroyo Quemado (AQUE)", "Naples (NAPL)", "Isla Vista (IVEE)", "Mohawk (MOHK)", "Carpinteria (CARP)")) %>% 
  # create a new column for "kelp year"
  mutate(quarter = fct_relevel(quarter, "Q2", "Q3", "Q4", "Q1")) %>% 
  mutate(kelp_year = case_when(
    quarter %in% c("Q2", "Q3", "Q4") ~ year,
    quarter == "Q1" ~ year - 1
  )) %>% 
  mutate(kelp_year = paste("kelp_", kelp_year, "-", kelp_year + 1, sep = "")) %>% 
  # create a column for the points to compare for "2 year interval"
  mutate(comp_2yrs = case_when(
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2008-2009", "kelp_2009-2010") ~ "start",
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2015-2016", "kelp_2016-2017") ~ "during", 
    site == "ivee" & kelp_year %in% c("kelp_2011-2012", "kelp_2012-2013") ~ "start",
    site == "ivee" & kelp_year %in% c("kelp_2015-2016", "kelp_2016-2017") ~ "during",
    kelp_year %in% c("kelp_2020-2021", "kelp_2021-2022") ~ "after"
  )) %>% 
  mutate(comp_2yrs = fct_relevel(comp_2yrs, "start", "during", "after")) %>% 
  # create a column for the points to compare for "3 year interval"
  mutate(comp_3yrs = case_when(
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2008-2009", "kelp_2009-2010", "kelp_2010-2011") ~ "start",
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2014-2015", "kelp_2015-2016", "kelp_2016-2017") ~ "during", 
    site == "ivee" & kelp_year %in% c("kelp_2011-2012", "kelp_2012-2013", "kelp_2013-2014") ~ "start",
    site == "ivee" & kelp_year %in% c("kelp_2014-2015", "kelp_2015-2016", "kelp_2016-2017") ~ "during",
    kelp_year %in% c("kelp_2019-2020", "kelp_2020-2021", "kelp_2021-2022") ~ "after"
  )) %>% 
  mutate(comp_3yrs = fct_relevel(comp_3yrs, "start", "during", "after"))

delta_continual <- delta_biomass %>% 
  dplyr::select(site, year, month, date, control, continual, delta_continual) %>% 
  # take out years where continual removal hadn't happened yet
  drop_na(delta_continual) %>% 
  mutate(exp_dates = case_when(
    # after for annual removal:
    site == "aque" & date >= aque_after_date_continual ~ "after",
    site == "napl" & date >= napl_after_date_continual ~ "after",
    site == "mohk" & date >= mohk_after_date_continual ~ "after",
    site == "carp" & date >= carp_after_date_continual ~ "after",
    # everything else is "during" the experiment
    TRUE ~ "during"
  ),
  exp_dates = fct_relevel(exp_dates, c("during", "after"))) %>% 
  # create a column for quarter
  mutate(quarter = case_when(
    month <= 3 ~ "Q1",
    month <= 6 ~ "Q2",
    month <= 9 ~ "Q3",
    TRUE ~ "Q4"
  )) %>% 
  # calculate time since start of experiment
  mutate(time_yrs = case_when(
    # AQUE, NAPL, MOHK, CARP: continual started in 2010
    quarter == "Q1" ~ year + 0.125 - 2010,
    quarter == "Q2" ~ year + 0.375 - 2010,
    quarter == "Q3" ~ year + 0.625 - 2010,
    quarter == "Q4" ~ year + 0.875 - 2010
  )) %>% 
  group_by(site) %>% 
  mutate(time_since_start = time_yrs - min(time_yrs)) %>% 
  ungroup() %>% 
  # calculate time since end of experiment
  group_by(site, exp_dates) %>% 
  mutate(time_since_end = case_when(
    exp_dates == "during" ~ -(max(time_yrs) + 0.25 - time_yrs),
    exp_dates == "after" ~ time_yrs - min(time_yrs)
  )) %>% 
  ungroup() %>% 
  left_join(., enframe(sites_full), by = c("site" = "name")) %>% 
  rename(site_full = value) %>% 
  mutate(site_full = fct_relevel(site_full, "Arroyo Quemado (AQUE)", "Naples (NAPL)", "Mohawk (MOHK)", "Carpinteria (CARP)")) %>% 
  # create a new column for "kelp year"
  mutate(quarter = fct_relevel(quarter, "Q2", "Q3", "Q4", "Q1")) %>% 
  mutate(kelp_year = case_when(
    quarter %in% c("Q2", "Q3", "Q4") ~ year,
    quarter == "Q1" ~ year - 1
  )) %>% 
  mutate(kelp_year = paste("kelp_", kelp_year, "-", kelp_year + 1, sep = "")) %>% 
  # create a column for the points to compare for "2 year interval"
  mutate(comp_2yrs = case_when(
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2010-2011", "kelp_2011-2012") ~ "start",
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2015-2016", "kelp_2016-2017") ~ "during", 
    site == "ivee" & kelp_year %in% c("kelp_2011-2012", "kelp_2012-2013") ~ "start",
    site == "ivee" & kelp_year %in% c("kelp_2015-2016", "kelp_2016-2017") ~ "during",
    kelp_year %in% c("kelp_2020-2021", "kelp_2021-2022") ~ "after"
  )) %>% 
  mutate(comp_2yrs = fct_relevel(comp_2yrs, "start", "during", "after")) %>% 
  # create a column for the points to compare for "3 year interval"
  mutate(comp_3yrs = case_when(
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2010-2011", "kelp_2011-2012", "kelp_2012-2013") ~ "start",
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2014-2015", "kelp_2015-2016", "kelp_2016-2017") ~ "during", 
    site == "ivee" & kelp_year %in% c("kelp_2011-2012", "kelp_2012-2013", "kelp_2013-2014") ~ "start",
    site == "ivee" & kelp_year %in% c("kelp_2014-2015", "kelp_2015-2016", "kelp_2016-2017") ~ "during",
    kelp_year %in% c("kelp_2019-2020", "kelp_2020-2021", "kelp_2021-2022") ~ "after"
  )) %>% 
  mutate(comp_3yrs = fct_relevel(comp_3yrs, "start", "during", "after")) %>% 
  # create a new sample ID that is site, year, quarter
  unite("sample_ID", site, year, quarter, remove = FALSE) %>% 
  # add a new column for the delta continual at the last experimental period
  mutate(delta_continual_end = case_when(
    site == "aque" ~ -383.9406750,
    site == "napl" ~ -1009.020417,
    site == "mohk" ~ -1625.65538,
    site == "carp" ~ -709.42300000
  )) %>% 
  left_join(., site_quality, by = "site")
  # # add a new column for the mean delta continual for the last 2 years of the experiment
  # group_by(site, comp_3yrs) %>% 
  # mutate(delta_continual_end_3yrs = case_when(
  #   comp_3yrs == "during" ~ mean(delta_continual)
  # )) %>% 
  # mutate(delta_continual_end_2yrs_test = case_when(
  #   site == "aque" ~ -257.79005,
  #   site == "napl" ~ -360.13564, 
  #   site == "mohk" ~ -722.17182,
  #   site == "carp" ~ -73.77815
  # ))
```

Delta annual and continual plots for kelp by section:

```{r}
# total biomass
kelp_biomass_section <- biomass_section %>% 
  filter(sp_code == "MAPY") %>% 
  dplyr::select(-sp_code) %>% 
  # make a new column for after dates
  after_dates_column() %>% 
  # make a new column for during and after and set factor levels
  exp_dates_column()
  # select(site, year, month, treatment, date, wm_gm2)

# delta biomass
delta_biomass_section <- kelp_biomass_section %>% 
  dplyr::select(site, year, month, treatment, date, quad, side, exp_dates, dry_gm2) %>% 
  pivot_wider(names_from = treatment, values_from = dry_gm2) %>% 
  mutate(delta_annual = annual - control,
         delta_continual = continual - control) 

delta_annual_section <- delta_biomass_section %>% 
  dplyr::select(site, year, month, date, quad, side, control, annual, delta_annual) %>% 
  drop_na(delta_annual) %>% 
  mutate(exp_dates = case_when(
    # after for annual removal:
    site == "aque" & date >= aque_after_date_annual ~ "after",
    site == "napl" & date >= napl_after_date_annual ~ "after",
    site == "ivee" & date >= ivee_after_date_annual ~ "after",
    site == "mohk" & date >= mohk_after_date_annual ~ "after",
    site == "carp" & date >= carp_after_date_annual ~ "after",
    # everything else is "during" the experiment
    TRUE ~ "during"
  ),
  exp_dates = fct_relevel(exp_dates, c("during", "after"))) %>% 
   # create a column for quarter
  mutate(quarter = case_when(
    month <= 3 ~ "Q1",
    month <= 6 ~ "Q2",
    month <= 9 ~ "Q3",
    TRUE ~ "Q4"
  )) %>% 
  # calculate time since start of experiment
  mutate(time_yrs = case_when(
    # AQUE, NAPL, MOHK, CARP: control and annual started in 2008
    site %in% c("aque", "napl", "mohk", "carp") & quarter == "Q1" ~ year + 0.125 - 2008,
    site %in% c("aque", "napl", "mohk", "carp") & quarter == "Q2" ~ year + 0.375 - 2008,
    site %in% c("aque", "napl", "mohk", "carp") & quarter == "Q3" ~ year + 0.625 - 2008,
    site %in% c("aque", "napl", "mohk", "carp") & quarter == "Q4" ~ year + 0.875 - 2008, 
    # IVEE control and annual started in 2011
    site == "ivee" & quarter == "Q1" ~ year + 0.125 - 2011,
    site == "ivee" & quarter == "Q2" ~ year + 0.375 - 2011,
    site == "ivee" & quarter == "Q3" ~ year + 0.625 - 2011,
    site == "ivee" & quarter == "Q4" ~ year + 0.875 - 2011
    )) %>% 
  group_by(site) %>% 
  mutate(time_since_start = time_yrs - min(time_yrs)) %>% 
  ungroup() %>% 
  # calculate time since end of experiment
  group_by(site, exp_dates) %>% 
  # if "after", then simple: the time in years - the minimum time in years
  # if "during", then more complex: take the max time in years and add 0.25, then subtract the time in years
  mutate(time_since_end = case_when(
    exp_dates == "during" ~ -(max(time_yrs) + 0.25 - time_yrs),
    exp_dates == "after" ~ time_yrs - min(time_yrs)
  )) %>% 
  ungroup() %>% 
  left_join(., enframe(sites_full), by = c("site" = "name")) %>% 
  rename(site_full = value) %>% 
  mutate(site_full = fct_relevel(site_full, "Arroyo Quemado (AQUE)", "Naples (NAPL)", "Isla Vista (IVEE)", "Mohawk (MOHK)", "Carpinteria (CARP)")) %>% 
  # create a new column for "kelp year"
  mutate(quarter = fct_relevel(quarter, "Q2", "Q3", "Q4", "Q1")) %>% 
  mutate(kelp_year = case_when(
    quarter %in% c("Q2", "Q3", "Q4") ~ year,
    quarter == "Q1" ~ year - 1
  )) %>% 
  mutate(kelp_year = paste("kelp_", kelp_year, "-", kelp_year + 1, sep = "")) %>% 
  # create a column for the points to compare for "2 year interval"
  mutate(comp_2yrs = case_when(
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2008-2009", "kelp_2009-2010") ~ "start",
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2015-2016", "kelp_2016-2017") ~ "during", 
    site == "ivee" & kelp_year %in% c("kelp_2011-2012", "kelp_2012-2013") ~ "start",
    site == "ivee" & kelp_year %in% c("kelp_2015-2016", "kelp_2016-2017") ~ "during",
    kelp_year %in% c("kelp_2020-2021", "kelp_2021-2022") ~ "after"
  )) %>% 
  mutate(comp_2yrs = fct_relevel(comp_2yrs, "start", "during", "after")) %>% 
  # create a column for the points to compare for "3 year interval"
  mutate(comp_3yrs = case_when(
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2008-2009", "kelp_2009-2010", "kelp_2010-2011") ~ "start",
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2014-2015", "kelp_2015-2016", "kelp_2016-2017") ~ "during", 
    site == "ivee" & kelp_year %in% c("kelp_2011-2012", "kelp_2012-2013", "kelp_2013-2014") ~ "start",
    site == "ivee" & kelp_year %in% c("kelp_2014-2015", "kelp_2015-2016", "kelp_2016-2017") ~ "during",
    kelp_year %in% c("kelp_2019-2020", "kelp_2020-2021", "kelp_2021-2022") ~ "after"
  )) %>% 
  mutate(comp_3yrs = fct_relevel(comp_3yrs, "start", "during", "after"))

delta_continual_section <- delta_biomass_section %>% 
  dplyr::select(site, year, month, date, quad, side, control, continual, delta_continual) %>% 
  # take out years where continual removal hadn't happened yet
  drop_na(delta_continual) %>% 
  mutate(exp_dates = case_when(
    # after for annual removal:
    site == "aque" & date >= aque_after_date_continual ~ "after",
    site == "napl" & date >= napl_after_date_continual ~ "after",
    site == "mohk" & date >= mohk_after_date_continual ~ "after",
    site == "carp" & date >= carp_after_date_continual ~ "after",
    # everything else is "during" the experiment
    TRUE ~ "during"
  ),
  exp_dates = fct_relevel(exp_dates, c("during", "after"))) %>% 
  # create a column for quarter
  mutate(quarter = case_when(
    month <= 3 ~ "Q1",
    month <= 6 ~ "Q2",
    month <= 9 ~ "Q3",
    TRUE ~ "Q4"
  )) %>% 
  # calculate time since start of experiment
  mutate(time_yrs = case_when(
    # AQUE, NAPL, MOHK, CARP: continual started in 2010
    quarter == "Q1" ~ year + 0.125 - 2010,
    quarter == "Q2" ~ year + 0.375 - 2010,
    quarter == "Q3" ~ year + 0.625 - 2010,
    quarter == "Q4" ~ year + 0.875 - 2010
  )) %>% 
  group_by(site) %>% 
  mutate(time_since_start = time_yrs - min(time_yrs)) %>% 
  ungroup() %>% 
  # calculate time since end of experiment
  group_by(site, exp_dates) %>% 
  mutate(time_since_end = case_when(
    exp_dates == "during" ~ -(max(time_yrs) + 0.25 - time_yrs),
    exp_dates == "after" ~ time_yrs - min(time_yrs)
  )) %>% 
  ungroup() %>% 
  left_join(., enframe(sites_full), by = c("site" = "name")) %>% 
  rename(site_full = value) %>% 
  mutate(site_full = fct_relevel(site_full, "Arroyo Quemado (AQUE)", "Naples (NAPL)", "Mohawk (MOHK)", "Carpinteria (CARP)")) %>% 
  # create a new column for "kelp year"
  mutate(quarter = fct_relevel(quarter, "Q2", "Q3", "Q4", "Q1")) %>% 
  mutate(kelp_year = case_when(
    quarter %in% c("Q2", "Q3", "Q4") ~ year,
    quarter == "Q1" ~ year - 1
  )) %>% 
  mutate(kelp_year = paste("kelp_", kelp_year, "-", kelp_year + 1, sep = "")) %>% 
  # create a column for the points to compare for "2 year interval"
  mutate(comp_2yrs = case_when(
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2010-2011", "kelp_2011-2012") ~ "start",
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2015-2016", "kelp_2016-2017") ~ "during", 
    site == "ivee" & kelp_year %in% c("kelp_2011-2012", "kelp_2012-2013") ~ "start",
    site == "ivee" & kelp_year %in% c("kelp_2015-2016", "kelp_2016-2017") ~ "during",
    kelp_year %in% c("kelp_2020-2021", "kelp_2021-2022") ~ "after"
  )) %>% 
  mutate(comp_2yrs = fct_relevel(comp_2yrs, "start", "during", "after")) %>% 
  # create a column for the points to compare for "3 year interval"
  mutate(comp_3yrs = case_when(
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2010-2011", "kelp_2011-2012", "kelp_2012-2013") ~ "start",
    site %in% c("aque", "napl", "mohk", "carp") & kelp_year %in% c("kelp_2014-2015", "kelp_2015-2016", "kelp_2016-2017") ~ "during", 
    site == "ivee" & kelp_year %in% c("kelp_2011-2012", "kelp_2012-2013", "kelp_2013-2014") ~ "start",
    site == "ivee" & kelp_year %in% c("kelp_2014-2015", "kelp_2015-2016", "kelp_2016-2017") ~ "during",
    kelp_year %in% c("kelp_2019-2020", "kelp_2020-2021", "kelp_2021-2022") ~ "after"
  )) %>% 
  mutate(comp_3yrs = fct_relevel(comp_3yrs, "start", "during", "after"))
```


## Plotting

### Before/after comparison

This creates plots where the mean kelp frond density is plotted for the "before" and "after" time points ("before" = during the experiment, and "after" = after the experiment ended). 

#### Frond density
```{r}
comparison_frond_fxn <- function(site_choice) {
  plot_title <- if(site_choice == "aque") {
    aque_full
  } else if(site_choice == "napl") {
    napl_full
  } else if(site_choice == "carp") {
    carp_full
  } else if(site_choice == "ivee") {
    ivee_full
  } else if(site_choice == "mohk") {
    mohk_full
  }
  
  total_fronds %>% 
    filter(site == site_choice) %>% 
    ggplot(aes(x = exp_dates, y = total_fronds, col = treatment, shape = treatment)) +
    # stat summary for point and SE for mean frond density during and after with line
    stat_summary(aes(group = treatment), fun = mean, geom = "line", size = 1, alpha = 0.8) +
    stat_summary(fun = mean, geom = "point", size = 4) +
    stat_summary(fun.data = mean_se, geom = "errorbar", alpha = 0.8, width = 0.2) +
    scale_color_manual(values = color_palette) +
    scale_shape_manual(values = shape_palette) +
    theme_bw() +
    theme(plot.title = element_text(size = 20)) +
    labs(x = " ",
         y = "Mean frond density",
         title = plot_title) 
}

aque_comparison_frond <- comparison_frond_fxn("aque")
mohk_comparison_frond <- comparison_frond_fxn("mohk")
carp_comparison_frond <- comparison_frond_fxn("carp")
ivee_comparison_frond <- total_fronds %>% 
    filter(site == "ivee") %>% 
    ggplot(aes(x = exp_dates, y = total_fronds, col = treatment, shape = treatment)) +
    stat_summary(aes(group = treatment), fun = mean, geom = "line", size = 1, alpha = 0.8) +
    stat_summary(fun = mean, geom = "point", size = 4) +
    stat_summary(fun.data = mean_se, geom = "errorbar", alpha = 0.8, width = 0.2) +
    scale_color_manual(values = color_palette) +
    scale_shape_manual(values = shape_palette) +
    theme_bw() +
    theme(plot.title = element_text(size = 20)) +
    labs(x = " ",
         y = "Mean frond density",
         title = ivee_full)
napl_comparison_frond <- comparison_frond_fxn("napl")

aque_comparison_frond
mohk_comparison_frond
carp_comparison_frond
ivee_comparison_frond
napl_comparison_frond
```

#### Kelp biomass
```{r}
comparison_biomass_fxn <- function(site_choice) {
  plot_title <- pluck(sites_full, site_choice)
  
  kelp_biomass %>% 
    filter(site == site_choice) %>% 
    ggplot(aes(x = exp_dates, y = wm_gm2, col = treatment, shape = treatment)) +
    stat_summary(aes(group = treatment), fun = mean, geom = "line", size = 1, alpha = 0.8, na.rm = TRUE) +
    stat_summary(fun = mean, geom = "point", size = 5, na.rm = TRUE) +
    
    stat_summary(fun.data = mean_se, geom = "errorbar", size = 1, width = 0.2, na.rm = TRUE) +
    scale_color_manual(values = color_palette) +
    scale_shape_manual(values = shape_palette) +
    theme_bw() +
    theme(plot.title = element_text(size = 20),
          axis.text = element_text(size = 16),
          axis.title = element_text(size = 18),
          legend.text = element_text(size = 14),
          legend.title = element_text(size = 14)) +
    labs(x = " ",
         y = "Mean kelp biomass (wm g/m2)",
         title = plot_title,
         col = "Treatment", shape = "Treatment")
}

aque_comparison_biomass <- comparison_biomass_fxn("aque")
napl_comparison_biomass <- comparison_biomass_fxn("napl")
ivee_comparison_biomass <- comparison_biomass_fxn("ivee")
mohk_comparison_biomass <- comparison_biomass_fxn("mohk")
carp_comparison_biomass <- comparison_biomass_fxn("carp")

aque_comparison_biomass
napl_comparison_biomass
ivee_comparison_biomass
mohk_comparison_biomass
carp_comparison_biomass
```

### best model for kelp frond density
```{r}
summary(aov(data = total_fronds,
    formula = total_fronds ~ treatment + site))

TukeyHSD(aov(data = total_fronds,
    formula = total_fronds ~ site + treatment + site*treatment))

model.dredge <- dredge(
  lm(total_fronds ~ site + treatment + site*treatment, data = total_fronds, na.action = na.pass)
)

model.sel(model.dredge) %>% 
  gt() %>% 
  tab_header(title = "all model subsets",
             subtitle = "total_fronds ~ site + treatment + site*treatment") 
# %>% 
#   gtsave("tab_1.png", expand = 10,
#          path = here::here("tables", "kelp_frond_model.png"))
```

### best model for kelp biomass

```{r}
summary(aov(data = kelp_biomass,
    formula = wm_gm2 ~ site + treatment + site*treatment))

TukeyHSD(aov(data = kelp_biomass,
    formula = wm_gm2 ~ site + treatment + site*treatment))

model.dredge <- dredge(
  lm(wm_gm2 ~ site + treatment + site*treatment, data = kelp_biomass, na.action = na.pass)
)

model.sel(model.dredge) %>% 
  gt() %>% 
  tab_header(title = "all model subsets",
             subtitle = "kelp_biomass ~ site + treatment + site*treatment") 
```

### Total kelp frond timeseries

This creates a plot where kelp frond density timeseries are plotted for each LTE site with control in open circles, annual in green circles, and continual in blue triangles. There is a `ggsave()` command at the end - **remember to change the date in the file name before saving**.

```{r}
total_frond_timeseries_fxn <- function(site_choice) {
  after_date <- if(site_choice == "aque") {
    aque_after_date_continual
  } else if(site_choice == "napl") {
    napl_after_date_continual
  } else if(site_choice == "carp") {
    carp_after_date_continual
  } else if(site_choice == "ivee") {
    ivee_after_date_continual
  } else if(site_choice == "mohk") {
    mohk_after_date_continual
  }
  
  plot_title <- if(site_choice == "aque") {
    aque_full
  } else if(site_choice == "napl") {
    napl_full
  } else if(site_choice == "carp") {
    carp_full
  } else if(site_choice == "ivee") {
    ivee_full
  } else if(site_choice == "mohk") {
    mohk_full
  }
  
  rect_ymax <- total_fronds %>% filter(site == site_choice) %>% pull(total_fronds) %>% max()
  
  df <- total_fronds %>% filter(site == site_choice)
  
  ggplot(data = df,
         aes(x = date, y = total_fronds, color = treatment, shape = treatment)) +
    scale_x_date(limits = c(napl_start_date, as.Date("2022-02-02"))) +
    geom_hline(yintercept = 0, color = "grey") +
    annotate("rect", xmin = after_date, xmax = as.Date("2022-02-02"),
           ymin = -1, ymax = rect_ymax*1.05,
           alpha = 0.2) +
    geom_point(size = 3) +
    geom_line(size = 1) +
    scale_color_manual(values = color_palette) +
    scale_shape_manual(values = shape_palette)  +
    theme_bw() + 
    labs(title = plot_title,
         x = " ",
         y = " ")
}

aque_total_frond_timeseries <- total_frond_timeseries_fxn("aque")
mohk_total_frond_timeseries <- total_frond_timeseries_fxn("mohk")
carp_total_frond_timeseries <- total_frond_timeseries_fxn("carp")
ivee_total_frond_timeseries <- ggplot(data = total_fronds %>% filter(site == "ivee"),
         aes(x = date, y = total_fronds, color = treatment, shape = treatment)) +
    scale_x_date(limits = c(napl_start_date, as.Date("2022-02-02"))) +
    geom_hline(yintercept = 0, color = "grey") +
    annotate("rect", xmin = ivee_after_date, xmax = as.Date("2022-02-02"),
           ymin = -1, ymax = (total_fronds %>% filter(site == "ivee") %>% pull(total_fronds) %>% max())*1.05,
           alpha = 0.2) +
    geom_point(size = 3) +
    geom_line(size = 1) +
    scale_color_manual(values = c("control" = control_col, "annual" = annual_col)) +
    scale_shape_manual(values = c("control" = control_shape, "annual" = annual_shape))  +
    theme_bw() + 
    labs(title = ivee_full,
         x = " ",
         y = " ")
napl_total_frond_timeseries <- total_frond_timeseries_fxn("napl")

aque_total_frond_timeseries
mohk_total_frond_timeseries
ivee_total_frond_timeseries
napl_total_frond_timeseries
carp_total_frond_timeseries

# y-axis label for patchwork side eye emoji
yaxislabel <- ggplot(data.frame(l = "kelp frond density", x = 1, y = 1)) +
      geom_text(aes(x, y, label = l), angle = 90) + 
      theme_void() +
      coord_cartesian(clip = "off")

plots_together <- yaxislabel + (aque_total_frond_timeseries / mohk_total_frond_timeseries / napl_total_frond_timeseries / ivee_total_frond_timeseries / carp_total_frond_timeseries) +
  plot_layout(guides = "collect", widths = c(1, 25)) &
  theme(legend.position = "bottom")

plots_together

# ggsave(here::here("figures", "kelp_total_frond_ts-20211012.jpg"), plots_together, height = 9, width = 5, dpi = 200)
```

#### Total frond timeseries for report

```{r}
aque_total_frond_timeseries_labs <- aque_total_frond_timeseries + 
  labs(x = "Sampling date", y = "Total kelp fronds",
       title = "Total kelp fronds") +
  theme(legend.position = "none")
mohk_total_frond_timeseries_labs <- mohk_total_frond_timeseries + 
  labs(x = "Sampling date", y = "Total kelp fronds",
       title = "Total kelp fronds") +
  theme(legend.position = "none")
ivee_total_frond_timeseries_labs <- ivee_total_frond_timeseries + 
  labs(x = "Sampling date", y = "Total kelp fronds",
       title = "Total kelp fronds") +
  theme(legend.position = "none")
napl_total_frond_timeseries_labs <- napl_total_frond_timeseries + 
  labs(x = "Sampling date", y = "Total kelp fronds",
       title = "Total kelp fronds") +
  theme(legend.position = "none")
carp_total_frond_timeseries_labs <- carp_total_frond_timeseries + 
  labs(x = "Sampling date", y = "Total kelp fronds",
       title = "Total kelp fronds") +
  theme(legend.position = "none")
```

### Total kelp biomass timeseries

```{r}
kelp_biomass_timeseries_fxn <- function(site_choice) {
  after_date <- if(site_choice == "aque") {
    aque_after_date_continual
  } else if(site_choice == "napl") {
    napl_after_date_continual
  } else if(site_choice == "carp") {
    carp_after_date_continual
  } else if(site_choice == "ivee") {
    ivee_after_date_continual
  } else if(site_choice == "mohk") {
    mohk_after_date_continual
  }
  
  plot_title <- if(site_choice == "aque") {
    aque_full
  } else if(site_choice == "napl") {
    napl_full
  } else if(site_choice == "carp") {
    carp_full
  } else if(site_choice == "ivee") {
    ivee_full
  } else if(site_choice == "mohk") {
    mohk_full
  }
  
  rect_ymax <- kelp_biomass %>% filter(site == site_choice) %>% pull(wm_gm2) %>% na.omit %>%  max()
  
  df <- kelp_biomass %>% filter(site == site_choice) %>% drop_na(wm_gm2)
  
  ggplot(data = df,
         aes(x = date, y = wm_gm2, color = treatment, shape = treatment)) +
    scale_x_date(limits = c(napl_start_date, as.Date("2022-02-02"))) +
    geom_hline(yintercept = 0, color = "grey") +
    annotate("rect", xmin = after_date, xmax = as.Date("2022-02-02"),
           ymin = -1, ymax = rect_ymax*1.05,
           alpha = 0.2) +
    geom_point(size = 3) +
    geom_line(size = 1) +
    scale_color_manual(values = color_palette) +
    scale_shape_manual(values = shape_palette)  +
    theme_bw() + 
    theme(legend.position = "none") +
    labs(title = plot_title,
         x = "Sampling date",
         y = "Kelp biomass (wm g/m2)")
}

aque_kelp_biomass_timeseries <- kelp_biomass_timeseries_fxn("aque")
napl_kelp_biomass_timeseries <- kelp_biomass_timeseries_fxn("napl")
ivee_kelp_biomass_timeseries <- ggplot(data = kelp_biomass %>% 
                                          filter(site == "ivee"),
                                        aes(x = date, y = wm_gm2, color = treatment, shape = treatment)) +
  scale_x_date(limits = c(napl_start_date, as.Date("2022-02-02"))) +
  geom_hline(yintercept = 0, color = "grey") +
  annotate("rect", xmin = ivee_after_date_annual, xmax = as.Date("2022-02-02"),
           ymin = -1, ymax = (kelp_biomass %>% filter(site == "ivee") %>% pull(wm_gm2) %>% max())*1.05,
           alpha = 0.2) +
  geom_point(size = 3) +
  geom_line(size = 1) +
  scale_color_manual(values = c("control" = "grey", "annual" = annual_col, "continual" = continual_col)) +
  scale_shape_manual(values = c("control" = control_shape, "annual" = annual_shape, "continual" = continual_shape))  +
  theme_bw() + 
  theme(legend.position = "none") +
  labs(title = ivee_full,
       x = "Sampling date",
       y = "Total kelp biomass (wm g/m2)")
mohk_kelp_biomass_timeseries <- kelp_biomass_timeseries_fxn("mohk")
carp_kelp_biomass_timeseries <- kelp_biomass_timeseries_fxn("carp")

aque_kelp_biomass_timeseries
napl_kelp_biomass_timeseries
ivee_kelp_biomass_timeseries
mohk_kelp_biomass_timeseries
carp_kelp_biomass_timeseries
```

### Annual kelp biomass timeseries

```{r}
annual_biomass_timeseries <- kelp_biomass %>% 
  filter(treatment == "annual") %>% 
  group_by(site) %>% 
  mutate(site_label = case_when(
    date == last(date) ~ sites_full[as.character(site)],
    TRUE ~ ""
  )) %>% 
  ggplot(aes(x = date, y = wm_gm2)) +
    annotate("rect", xmin = as.Date("2017-01-01"), xmax = as.Date("2022-02-02"),
           ymin = -1, ymax = 10000,
           alpha = 0.2) +
  geom_point(aes(col = site), size = 3) +
  geom_line(aes(col = site), size = 1) +
  # geom_text(aes(label = site_label, col = site), hjust = 0.1, size = 4, vjust = 1, 
  #           label.padding = unit(0.25, "lines")) +
  scale_color_manual(values = site_palette) +
  labs(x = "Sampling date", y = "Kelp biomass (wm g/m2)",
       title = "Annual only") +
  theme_bw() +
  theme(panel.border = element_blank(),
        plot.title = element_text(size = 16)) 

  # geom_text(data = . %>% filter(date == max(date)),
  #           aes(color = Province_State, x = as.Date(Inf),
  #               y = deaths_roll7_100k),
  #           hjust = 0, size = 4, vjust = 0.7,
  #           label = c("Arizona\n", "North Carolina"))


annual_biomass_timeseries

# ggsave(here::here("figures", "annual_biomass_timeseries.jpg"), annual_biomass_timeseries, width = 14, height = 8, dpi = 300)
```


### Delta kelp frond timeseries

This creates a plot where delta kelp frond density (difference between control and removal density) timeseries are plotted for each LTE site with annual in green circles and continual in blue circles. This was supposed to be a recreation of the plots that Adrian sent a long time ago. There is a `ggsave()` command at the end - **remember to change the date in the file name before saving**.

```{r}
delta_frond_timeseries_fxn <- function(site_choice) {
  after_date <- if(site_choice == "aque") {
    aque_after_date
  } else if(site_choice == "napl") {
    napl_after_date
  } else if(site_choice == "carp") {
    carp_after_date
  } else if(site_choice == "ivee") {
    ivee_after_date
  } else if(site_choice == "mohk") {
    mohk_after_date
  }
  
  delta_continual_max <- delta_fronds %>% filter(site == site_choice) %>% pull(delta_continual) %>% max(na.rm = TRUE)
  delta_continual_min <- delta_fronds %>% filter(site == site_choice) %>% pull(delta_continual) %>% min(na.rm = TRUE)
  delta_annual_max <- delta_fronds %>% filter(site == site_choice) %>% pull(delta_annual) %>% max(na.rm = TRUE)  
  delta_annual_min <- delta_fronds %>% filter(site == site_choice) %>% pull(delta_annual) %>% min(na.rm = TRUE)
  
  rect_ymax <- ifelse(delta_continual_max > delta_annual_max, delta_continual_max, delta_annual_max)
  rect_ymin <- ifelse(delta_continual_min < delta_annual_max, delta_continual_min, delta_annual_max)
  
  ggplot() +
    scale_x_date(limits = c(napl_start_date, as.Date("2022-02-02"))) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
    annotate("rect", xmin = after_date, xmax = as.Date("2022-02-02"),
             ymin = rect_ymin*1.1, ymax = rect_ymax*1.1,
             alpha = 0.2) +
    annotate("text", x = as.Date("2009-04-01"), y = rect_ymax*1.1, label = "removal > control", size = 3) +
  annotate("text", x = as.Date("2009-04-01"), y = rect_ymin*1.1, label = "control > removal", size = 3) +
    geom_point(data = delta_fronds %>% filter(site == site_choice & delta_annual != "NA"), 
               aes(x = date, y = delta_annual, color = "annual"), 
               size = 3, shape = annual_shape) +
    geom_line(data = delta_fronds %>% filter(site == site_choice & delta_annual != "NA"),
              aes(x = date, y = delta_annual, color = "annual"), size = 1) +
    geom_point(data = delta_fronds %>% filter(site == site_choice & delta_continual != "NA"), 
               aes(x = date, y = delta_continual, color = "continual"), 
               size = 3, shape = continual_shape) +
    geom_line(data = delta_fronds %>% filter(site == site_choice & delta_continual != "NA"),
              aes(x = date, y = delta_continual, color = "continual"), size = 1) +
    scale_color_manual(name = NULL,
                       breaks = c("annual", "continual"),
                       values = c("annual" = annual_col, "continual" = continual_col)) +
    theme_bw() + 
    labs(title = site_choice,
         x = " ",
         y = " ")
}

aque_delta_kelp_timeseries <- delta_frond_timeseries_fxn("aque")
mohk_delta_kelp_timeseries <- delta_frond_timeseries_fxn("mohk")
carp_delta_kelp_timeseries <- delta_frond_timeseries_fxn("carp")
ivee_delta_kelp_timeseries <- ggplot() +
  scale_x_date(limits = c(napl_start_date, as.Date("2022-02-02"))) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
      annotate("rect", xmin = ivee_after_date, xmax = as.Date("2022-02-02"),
             ymin = delta_fronds %>% filter(site == "ivee") %>% pull(delta_annual) %>% min()*1.1, 
             ymax = delta_fronds %>% filter(site == "ivee") %>% pull(delta_annual) %>% max()*1.1,
             alpha = 0.2) +
  annotate("text", x = as.Date("2009-04-01"), y = delta_fronds %>% filter(site == "ivee") %>% pull(delta_annual) %>% max()*1.1, label = "removal > control", size = 3) +
  annotate("text", x = as.Date("2009-04-01"), y = delta_fronds %>% filter(site == "ivee") %>% pull(delta_annual) %>% min()*1.1, label = "control > removal", size = 3) +
  geom_point(data = delta_fronds %>% filter(site == "ivee" & delta_annual != "NA"), 
             aes(x = date, y = delta_annual), color = annual_col, size = 3) +
  geom_line(data = delta_fronds %>% filter(site == "ivee" & delta_annual != "NA"),
            aes(x = date, y = delta_annual), color = annual_col, size = 1) +
  theme_bw() + 
  labs(title = "ivee",
       x = "Sampling date",
       y = " ")
napl_delta_kelp_timeseries <- delta_frond_timeseries_fxn("napl")

aque_delta_kelp_timeseries
mohk_delta_kelp_timeseries
ivee_delta_kelp_timeseries
napl_delta_kelp_timeseries
carp_delta_kelp_timeseries

# y-axis label for patchwork side eye emoji
yaxislabel <- ggplot(data.frame(l = "kelp fronds (removal - control)", x = 1, y = 1)) +
      geom_text(aes(x, y, label = l), angle = 90) + 
      theme_void() +
      coord_cartesian(clip = "off")

plots_together <- yaxislabel + (aque_delta_kelp_timeseries / mohk_delta_kelp_timeseries / napl_delta_kelp_timeseries / ivee_delta_kelp_timeseries / carp_delta_kelp_timeseries) +
  plot_layout(guides = "collect", widths = c(1, 25)) &
  theme(legend.position = "bottom")

plots_together

# ggsave(here::here("figures", "kelp_frond_ts-20220201.jpg"), plots_together, height = 9, width = 5, dpi = 200)
```

#### Delta frond timeseries for report

```{r}
aque_delta_kelp_timeseries_labs <- aque_delta_kelp_timeseries +
  labs(x = "Sampling date", y = "\u0394 fronds \n (removal - control)",
       title = "\u0394 fronds (removal - control)")  +
  theme(legend.position = "none")
mohk_delta_kelp_timeseries_labs <- mohk_delta_kelp_timeseries +
  labs(x = "Sampling date", y = "\u0394 fronds \n (removal - control)",
       title = "\u0394 fronds (removal - control)")  +
  theme(legend.position = "none")
ivee_delta_kelp_timeseries_labs <- ivee_delta_kelp_timeseries +
  labs(x = "Sampling date", y = "\u0394 fronds \n (removal - control)",
       title = "\u0394 fronds (removal - control)")  +
  theme(legend.position = "none")
napl_delta_kelp_timeseries_labs <- napl_delta_kelp_timeseries +
  labs(x = "Sampling date", y = "\u0394 fronds \n (removal - control)",
       title = "\u0394 fronds (removal - control)")  +
  theme(legend.position = "none")
carp_delta_kelp_timeseries_labs <- carp_delta_kelp_timeseries +
  labs(x = "Sampling date", y = "\u0394 fronds \n (removal - control)",
       title = "\u0394 fronds (removal - control)") +
  theme(legend.position = "none")
```

### Delta biomass timeseries

```{r}
delta_biomass_timeseries_fxn <- function(site_choice) {
  after_date <- if(site_choice == "aque") {
    aque_after_date
  } else if(site_choice == "napl") {
    napl_after_date
  } else if(site_choice == "carp") {
    carp_after_date
  } else if(site_choice == "ivee") {
    ivee_after_date
  } else if(site_choice == "mohk") {
    mohk_after_date
  }
  
  plot_title <- pluck(sites_full, site_choice)
  
  delta_continual_max <- delta_biomass %>% filter(site == site_choice) %>% pull(delta_continual) %>% max(na.rm = TRUE)
  delta_continual_min <- delta_biomass %>% filter(site == site_choice) %>% pull(delta_continual) %>% min(na.rm = TRUE)
  delta_annual_max <- delta_biomass %>% filter(site == site_choice) %>% pull(delta_annual) %>% max(na.rm = TRUE)  
  delta_annual_min <- delta_biomass %>% filter(site == site_choice) %>% pull(delta_annual) %>% min(na.rm = TRUE)
  
  rect_ymax <- ifelse(delta_continual_max > delta_annual_max, delta_continual_max, delta_annual_max)
  rect_ymin <- ifelse(delta_continual_min < delta_annual_max, delta_continual_min, delta_annual_max)
  
  ggplot() +
    scale_x_date(limits = c(napl_start_date, as.Date("2022-02-02"))) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
    annotate("rect", xmin = after_date, xmax = as.Date("2022-02-02"),
             ymin = rect_ymin*1.1, ymax = rect_ymax*1.1,
             alpha = 0.2) +
    annotate("text", x = as.Date("2009-04-01"), y = rect_ymax*1.1, label = "removal > control", size = 3) +
  annotate("text", x = as.Date("2009-04-01"), y = rect_ymin*1.1, label = "control > removal", size = 3) +
    geom_point(data = delta_biomass %>% filter(site == site_choice & delta_annual != "NA"), 
               aes(x = date, y = delta_annual, color = "annual"), 
               size = 3, shape = annual_shape) +
    geom_line(data = delta_biomass %>% filter(site == site_choice & delta_annual != "NA"),
              aes(x = date, y = delta_annual, color = "annual"), size = 1) +
    geom_point(data = delta_biomass %>% filter(site == site_choice & delta_continual != "NA"), 
               aes(x = date, y = delta_continual, color = "continual"), 
               size = 3, shape = continual_shape) +
    geom_line(data = delta_biomass %>% filter(site == site_choice & delta_continual != "NA"),
              aes(x = date, y = delta_continual, color = "continual"), size = 1) +
    scale_color_manual(name = NULL,
                       breaks = c("annual", "continual"),
                       values = c("annual" = annual_col, "continual" = continual_col)) +
    theme_bw() + 
    theme(legend.position = "none") +
    labs(x = "Sampling date",
         y = "\u0394 kelp biomass \n (wm g/m2, removal - control)",
         title = plot_title)
}

aque_delta_biomass_timeseries <- delta_biomass_timeseries_fxn("aque")
napl_delta_biomass_timeseries <- delta_biomass_timeseries_fxn("napl")
ivee_delta_biomass_timeseries <- ggplot() +
  scale_x_date(limits = c(napl_start_date, as.Date("2022-02-02"))) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
  annotate("rect", xmin = ivee_after_date, xmax = as.Date("2022-02-02"),
           ymin = delta_biomass %>% filter(site == "ivee") %>% pull(delta_annual) %>% min()*1.1, 
           ymax = delta_biomass %>% filter(site == "ivee") %>% pull(delta_annual) %>% max()*1.1,
           alpha = 0.2) +
  annotate("text", x = as.Date("2009-04-01"), y = delta_biomass %>% filter(site == "ivee") %>% pull(delta_annual) %>% max()*1.1, label = "removal > control", size = 3) +
  annotate("text", x = as.Date("2009-04-01"), y = delta_biomass %>% filter(site == "ivee") %>% pull(delta_annual) %>% min()*1.1, label = "control > removal", size = 3) +
  geom_point(data = delta_biomass %>% filter(site == "ivee" & delta_annual != "NA"), 
             aes(x = date, y = delta_annual, color = "annual"), 
             size = 3, shape = annual_shape) +
  geom_line(data = delta_biomass %>% filter(site == "ivee" & delta_annual != "NA"),
            aes(x = date, y = delta_annual, color = "annual"), size = 1) +
  scale_color_manual(name = NULL,
                     breaks = c("annual"),
                     values = c("annual" = annual_col)) +
  theme_bw() + 
  theme(legend.position = "none") +
  labs(x = "Sampling date",
       y = "\u0394 kelp biomass \n (wm g/m2, removal - control)",
       title = "ivee")
mohk_delta_biomass_timeseries <- delta_biomass_timeseries_fxn("mohk")
carp_delta_biomass_timeseries <- delta_biomass_timeseries_fxn("carp")


aque_delta_biomass_timeseries
napl_delta_biomass_timeseries
ivee_delta_biomass_timeseries
mohk_delta_biomass_timeseries
carp_delta_biomass_timeseries
```

### 2022-02-04 report figures

```{r}
aque_panels <- (aque_comparison_frond / aque_total_frond_timeseries_labs / aque_delta_kelp_timeseries_labs) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(size = 16))

napl_panels <- (napl_comparison_frond / napl_total_frond_timeseries_labs / napl_delta_kelp_timeseries_labs) +
  plot_layout(guides = "collect") 

ivee_panels <- (ivee_comparison_frond / ivee_total_frond_timeseries_labs / ivee_delta_kelp_timeseries_labs) +
  plot_layout(guides = "collect") 

carp_panels <- (carp_comparison_frond / carp_total_frond_timeseries_labs / carp_delta_kelp_timeseries_labs) +
  plot_layout(guides = "collect") 

mohk_panels <- (mohk_comparison_frond / mohk_total_frond_timeseries_labs / mohk_delta_kelp_timeseries_labs) +
  plot_layout(guides = "collect") 

# ggsave(here::here("figures", "panels_aque_2022-02-03.jpg"), aque_panels, height = 10, width = 9, dpi = 300)
# 
# ggsave(here::here("figures", "panels_napl_2022-02-03.jpg"), napl_panels, height = 10, width = 9, dpi = 300)
# 
# ggsave(here::here("figures", "panels_ivee_2022-02-03.jpg"), ivee_panels, height = 10, width = 9, dpi = 300)
# 
# ggsave(here::here("figures", "panels_carp_2022-02-03.jpg"), carp_panels, height = 10, width = 9, dpi = 300)
# 
# ggsave(here::here("figures", "panels_mohk_2022-02-03.jpg"), mohk_panels, height = 10, width = 9, dpi = 300)
```

### 2022-02-11 report figures

```{r}
aque_panels <- (aque_comparison_biomass / aque_kelp_biomass_timeseries / aque_delta_biomass_timeseries) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(size = 16))

napl_panels <- (napl_comparison_biomass / napl_kelp_biomass_timeseries / napl_delta_biomass_timeseries) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(size = 16))

ivee_panels <- (ivee_comparison_biomass / ivee_kelp_biomass_timeseries / ivee_delta_biomass_timeseries) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(size = 16))

carp_panels <- (carp_comparison_biomass / carp_kelp_biomass_timeseries / carp_delta_biomass_timeseries) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(size = 16))

mohk_panels <- (mohk_comparison_biomass / mohk_kelp_biomass_timeseries / mohk_delta_biomass_timeseries) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(size = 16))

# ggsave(here::here("figures", "panels_biomass_aque_2022-02-08.jpg"), aque_panels, height = 10, width = 9, dpi = 300)
# 
# ggsave(here::here("figures", "panels_biomass_napl_2022-02-08.jpg"), napl_panels, height = 10, width = 9, dpi = 300)
# 
# ggsave(here::here("figures", "panels_biomass_ivee_2022-02-08.jpg"), ivee_panels, height = 10, width = 9, dpi = 300)
# 
# ggsave(here::here("figures", "panels_biomass_carp_2022-02-08.jpg"), carp_panels, height = 10, width = 9, dpi = 300)
# 
# ggsave(here::here("figures", "panels_biomass_mohk_2022-02-08.jpg"), mohk_panels, height = 10, width = 9, dpi = 300)
```


## Model selection for delta frond density

Using function from the Thiault script below. Made edits to not print out results in the quartz viewer.

```{r}
ProgressiveChangeBACIPS<-function(control, impact, time.true, time.model) 
{
	### STEP 2 - Calculate the delta at each sampling date
	delta <- impact - control
	
	# Plot delta against time.true
	# dev.new(width=10, height=5)
	# par(mfrow=c(1,2))
	plot(delta~time.true, type="n")
	time.model.of.impact=max(which(time.model==0))
	rect(time.model.of.impact, min(delta)-100, max(time.model)+10, max(delta)+100, col = "grey")
	points(delta~time.true, pch=24, bg="white", cex=2)
	
	### STEP 3 - Fit and compete models
	## Create a 'period' variable: if the time model == 0, assign "before"
	## otherwise, assign "after"
	## this is the only predictor in the aov() call below
	period <- ifelse(time.model == 0, "Before", "After")
	
	## Fit a step model
	# analysis of variance: comparing means
	step.Model<-aov(delta ~ period)

	## Fit a linear model
	# linear model: delta as a function of time.model
	# 0s in "before", sequence of numbers in "after"
	linear.Model<-lm(delta ~ time.model)
	
	## Fit an asymptotic model
	# Create an asymptotic function
	myASYfun<-function(delta, time.model)
	{
		funAsy<-function(parS, time.model)	(parS$M * time.model) / (parS$L + time.model) + parS$B
		residFun<-function(p, observed, time.model) observed + funAsy(p,time.model)
		parStart <- list(M=mean(delta[time.model.of.impact:length(time.true)]), B=mean(delta[1:time.model.of.impact]), L=1)
		nls_ASY_out <- nls.lm(par=parStart, fn= residFun, observed=delta, time.model=time.model, control = nls.lm.control(maxfev = integer(), maxiter = 1000))
		foAsy<-delta~(M * time.model) / (L + time.model) + B
		startPar<-c(-coef(nls_ASY_out)[1], coef(nls_ASY_out)[2], coef(nls_ASY_out)[3])
		asyFit<-nls2(foAsy, start=startPar, algorithm="brute-force") # nls2 enables to calculate AICc
		asyFit
	}
	# Fit the asymptotic model
	asymptotic.Model<-myASYfun(delta=delta,time.model=time.model)
	
	
	## Fit a sigmoid model
	## Create a sigmoid function
	mySIGfun<-function(delta, time.model)
	{
		funSIG<-function(parS, time.model)	(parS$M * (time.model/parS$L)^parS$K) / (1 + (time.model/parS$L) ^ parS$K) + parS$B
		residFun<-function(p, observed, time.model) observed + funSIG(p,time.model)
		parStart <- list(M=mean(delta[time.model.of.impact:length(time.true)]), B=mean(delta[1:time.model.of.impact]), L=mean(time.model), K=5)
		nls_SIG_out <- nls.lm(par=parStart, fn= residFun, observed=delta, time.model=time.model, control = nls.lm.control(maxfev = integer(), maxiter = 1000))
		foSIG<-delta~(M * (time.model/L) ^ K) / (1 + (time.model/L) ^ K) + B
		startPar<-c(-coef(nls_SIG_out)[1],-coef(nls_SIG_out)[2],coef(nls_SIG_out)[3],coef(nls_SIG_out)[4])
		sigFit<-nls2(foSIG, start=startPar, algorithm="brute-force") # nls2 enables to calculate AICc
		sigFit
	}
	# Fit the sigmoid model
	sigmoid.Model<-mySIGfun(delta=delta,time.model=time.model)


	## Compete models
	# Perform AIC tests
	AIC.test<-AIC(step.Model, linear.Model, asymptotic.Model, sigmoid.Model)
	AICc.test<-as.data.frame(cbind(AIC.test[,1], c(AICc(step.Model), AICc(linear.Model), AICc(asymptotic.Model), AICc(sigmoid.Model))))
	rownames(AICc.test)<-rownames(AIC.test)
	names(AICc.test)<-names(AIC.test)
	
	# Calculate AICc weight and selected the best model
	for(i in 1:dim(AICc.test)[1])
	{
		AICc.test$diff[i]<-AICc.test$AIC[i]-min(AICc.test$AIC)
	}
	AICc.test$RL<-exp(-0.5* AICc.test$diff)
	RL_sum<-sum(AICc.test$RL)
	AICc.test$aicWeights<-(AICc.test$RL/RL_sum)*100
	w<-AICc.test$aicWeights
	names(w)<-rownames(AICc.test)
	
	# Display raw AIC values
	print(AICc.test)

	# Display AICc weights
	# print(w)
	barplot(w, col="white", ylab="Relative likelihood (%)", cex.names = 0.9, names.arg =c("Step","Linear","Asymptotic","Sigmoid"))
	best.Model<-which(w==max(w))
	
	model.formula <- if(best.Model==1) {
	  step.Model
	} else if(best.Model==2) {
	  linear.Model
	} else if(best.Model==3) {
	  asymptotic.Model
	} else if(best.Model==4) {
	  sigmoid.Model
	}
	
	message <- if(best.Model==1) {
	  "Step"
	} else if(best.Model==2) {
	  "Linear"
	} else if(best.Model==3) {
	  "Asymptotic"
	} else if(best.Model==4) {
	  "Sigmoid"
	}
	
	likelihood <- if(best.Model==1) {
	  paste(round(w[1],1), "%", sep="")
	} else if(best.Model==2) {
	  paste(round(w[2],1), "%", sep="")
	} else if(best.Model==3) {
	  paste(round(w[3],1), "%", sep="")
	} else if(best.Model==4) {
	  paste(round(w[4],1), "%", sep="")
	}
	  
	### STEP 4 - Derive inference based on the best model (i.e., with the higher AICc weight)
	if(best.Model==1) {writeLines(paste("\n\nSTEP MODEL SELECTED - Likelihood = ", round(w[1],1), "%\n\n", sep=""))
		print(summary(step.Model))}
	if(best.Model==2) {writeLines(paste("\n\nLINEAR MODEL SELECTED - Likelihood = ", round(w[2],1), "%\n\n", sep=""))
		print(summary(linear.Model))}
	if(best.Model==3) {writeLines(paste("\n\nASYMPTOTIC MODEL SELECTED - Likelihood = ", round(w[3],1), "%\n\n", sep=""))
		print(asymptotic.Model)}
	if(best.Model==4) {writeLines(paste("\n\nSIGMOID MODEL SELECTED - Likelihood = ", round(w[4],1), "%\n\n", sep=""))
		print(sigmoid.Model)}
	
	return(c(message = message,
	         likelihood = likelihood,
	         aicc.test.results = AICc.test, 
	         step.model.summary = summary(step.Model), 
	         linear.model.summary = summary(linear.Model), 
	         asy.model.summary = asymptotic.Model, 
	         sigmoid.model.summary = sigmoid.Model))
}

```

Function to add a column in the biomass data frame for each site called `time.model` that has the timesteps labelled the way the function wants them.

```{r}
time.model.fxn.new <- function(site, treatment, season_choice) {
  # select a data frame based on site and treatment
  df <- if(treatment == "annual") {
    delta_annual
  } else if(treatment == "continual") {
    delta_continual
  } else {
    warning("Check your arguments! You might be missing site, treatment, or season.")
  }
  
  season_choice <- if(season_choice == "all") {
    c("winter", "spring", "summer", "fall")
  } else if(season_choice == "summer") {
    c("summer")
  } else if (season_choice == "fall") {
    c("fall")
  } else if (season_choice == "winter") {
    c("winter")
  } else if (season_choice == "spring") {
    c("spring")
  } else {
    warning("Check your arguments! You might be missing site, treatment, or season.")
    return(NA)
  }
  
  df %>% 
  filter(site == {{ site }}) %>% 
  dplyr::select(site, year, month, date, control, annual, exp_dates, contains("delta_"), time_since_end) %>% 
  mutate(exp_dates = fct_relevel(exp_dates, c("after", "during"))) %>% 
  arrange(exp_dates) %>% 
  # assign everything a "time step number" using the row numbers...
  rownames_to_column("time.model") %>% 
  # only keep the time step numbers for the "after dates"
  # make everything else 0 (i.e. everything else is before the "after")
  mutate(time.model = case_when(
    exp_dates == "during" ~ 0,
    TRUE ~ as.numeric(as.numeric(time.model))
  )) %>% 
  # rearrange the sampling dates to be in logical order
  mutate(exp_dates = fct_relevel(exp_dates, c("during", "after"))) %>% 
  arrange(exp_dates) 
}

biomass.pcbacips <- function(df) {
  ProgressiveChangeBACIPS(
    control = pull(df, 6), # control column
    impact = pull(df, 7), # treatment column
    time.true = pull(df, 5), # date column
    time.model = pull(df, 1) # time.model column
  )
}
```

### Figures

For reference.
```{r}
delta_annual_plot
delta_continual_plot
```


### Arroyo Quemado

**Notes to self**: maybe the ProgressiveChangeBACIPS is useful for figuring out what is happening in removal plots post-experiment-end relative to during the experiment. For example, it's useful to know when the change is a step change as opposed to a linear change. However, the linear model approximation is not great - that might be due to the model formulation, but probably not. 

```{r}
aque_biomass_annual <- time.model.fxn.new("aque", "annual", "all")
aque_biomass_annual_summer <- time.model.fxn.new("aque", "annual", "summer")
aque_biomass_annual_fall <- time.model.fxn.new("aque", "annual", "fall")

aque_biomass_continual <- time.model.fxn.new("aque", "continual", "all")
aque_biomass_continual_summer <- time.model.fxn.new("aque", "continual", "summer")
aque_biomass_continual_fall <- time.model.fxn.new("aque", "continual", "fall")

aque_annual_bacips_results <- biomass.pcbacips(aque_biomass_annual)

# STEP MODEL SELECTED - Likelihood = 62.2%

control_bio <- aque_biomass_annual$control
annual_bio <- aque_biomass_annual$annual
delta_bio <- annual_bio - control_bio
TukeyHSD(aov(delta_bio ~ aque_biomass_annual$exp_dates))

aque_continual_bacips_results <- biomass.pcbacips(aque_biomass_continual)

# LINEAR MODEL SELECTED - Likelihood = 75%

aque_annual_bacips_results_summer <- biomass.pcbacips(aque_biomass_annual_summer)
# STEP MODEL SELECTED - Likelihood = 62.3%

aque_continual_bacips_results_summer <- biomass.pcbacips(aque_biomass_continual_summer)
# LINEAR MODEL SELECTED - Likelihood = 54.3%

aque_annual_bacips_results_fall <- biomass.pcbacips(aque_biomass_annual_fall)
# STEP MODEL SELECTED - Likelihood = 45.9%

aque_continual_bacips_results_fall <- biomass.pcbacips(aque_biomass_continual_fall)
# LINEAR MODEL SELECTED - Likelihood = 71.9%
```



### Naples

```{r}
napl_biomass_annual <- time.model.fxn.new("napl", "annual", "all")
napl_biomass_annual_summer <- time.model.fxn.new("napl", "annual", "summer")
napl_biomass_annual_fall <- time.model.fxn.new("napl", "annual", "fall")

napl_biomass_continual <- time.model.fxn.new("napl", "continual", "all")
napl_biomass_continual_summer <- time.model.fxn.new("napl", "continual", "summer")
napl_biomass_continual_fall <- time.model.fxn.new("napl", "continual", "fall")

napl_annual_bacips_results <- biomass.pcbacips(napl_biomass_annual)

# LINEAR MODEL SELECTED - Likelihood = 47.8%

napl_continual_bacips_results <- biomass.pcbacips(napl_biomass_continual)

# LINEAR MODEL SELECTED - Likelihood = 54.6%

napl_annual_bacips_results_summer <- biomass.pcbacips(napl_biomass_annual_summer)

# STEP MODEL SELECTED - Likelihood = 60.6%

napl_continual_bacips_results_summer <- biomass.pcbacips(napl_biomass_continual_summer)
# LINEAR MODEL SELECTED - Likelihood = 67.5%

napl_annual_bacips_results_fall <- biomass.pcbacips(napl_biomass_annual_fall)
# LINEAR MODEL SELECTED - Likelihood = 50.1%

napl_continual_bacips_results_fall <- biomass.pcbacips(napl_biomass_continual_fall)
# LINEAR MODEL SELECTED - Likelihood = 76.3%
```

### Isla Vista

```{r}
ivee_biomass_annual <- time.model.fxn.new("ivee", "annual", "all")
ivee_biomass_annual_summer <- time.model.fxn.new("ivee", "annual", "summer")
ivee_biomass_annual_fall <- time.model.fxn.new("ivee", "annual", "fall")

ivee_annual_bacips_results <- biomass.pcbacips(ivee_biomass_annual)
# STEP MODEL SELECTED - Likelihood = 92.5%

ivee_annual_bacips_results_summer <- biomass.pcbacips(ivee_biomass_annual_summer)

# STEP MODEL SELECTED - Likelihood = 60.6%

ivee_annual_bacips_results_fall <- biomass.pcbacips(ivee_biomass_annual_fall)

# STEP MODEL SELECTED - Likelihood = 63.2%
```

### Mohawk

```{r}
mohk_biomass_annual <- time.model.fxn.new("mohk", "annual", "all")
mohk_biomass_annual_summer <- time.model.fxn.new("mohk", "annual", "summer")
mohk_biomass_annual_fall <- time.model.fxn.new("mohk", "annual", "fall")

mohk_biomass_continual <- time.model.fxn.new("mohk", "continual", "all")
mohk_biomass_continual_summer <- time.model.fxn.new("mohk", "continual", "summer")
mohk_biomass_continual_fall <- time.model.fxn.new("mohk", "continual", "fall")

mohk_annual_bacips_results <- biomass.pcbacips(mohk_biomass_annual)
# INEAR MODEL SELECTED - Likelihood = 48%

mohk_continual_bacips_results <- biomass.pcbacips(mohk_biomass_continual)

# LINEAR MODEL SELECTED - Likelihood = 85.3%

mohk_annual_bacips_results_summer <- biomass.pcbacips(mohk_biomass_annual_summer)

# LINEAR MODEL SELECTED - Likelihood = 62.3%

mohk_continual_bacips_results_summer <- biomass.pcbacips(mohk_biomass_continual_summer)
# LINEAR MODEL SELECTED - Likelihood = 88.9%

mohk_annual_bacips_results_fall <- biomass.pcbacips(mohk_biomass_annual_fall)
# STEP MODEL SELECTED - Likelihood = 51%

mohk_continual_bacips_results_fall <- biomass.pcbacips(mohk_biomass_continual_fall)
# LINEAR MODEL SELECTED - Likelihood = 81.6%
```

### Carpinteria

```{r}
carp_biomass_annual <- time.model.fxn.new("carp", "annual", "all")
carp_biomass_annual_summer <- time.model.fxn.new("carp", "annual", "summer")
carp_biomass_annual_fall <- time.model.fxn.new("carp", "annual", "fall")

carp_biomass_continual <- time.model.fxn.new("carp", "continual", "all")
carp_biomass_continual_summer <- time.model.fxn.new("carp", "continual", "summer")
carp_biomass_continual_fall <- time.model.fxn.new("carp", "continual", "fall")

carp_annual_bacips_results <- biomass.pcbacips(carp_biomass_annual)

# LINEAR MODEL SELECTED - Likelihood = 52.9%

carp_continual_bacips_results <- biomass.pcbacips(carp_biomass_continual)

# LINEAR MODEL SELECTED - Likelihood = 48.6%

carp_annual_bacips_results_summer <- biomass.pcbacips(carp_biomass_annual_summer)

# STEP MODEL SELECTED - Likelihood = 48.5%

carp_continual_bacips_results_summer <- biomass.pcbacips(carp_biomass_continual_summer)
# STEP MODEL SELECTED - Likelihood = 50.3%

carp_annual_bacips_results_fall <- biomass.pcbacips(carp_biomass_annual_fall)
# STEP MODEL SELECTED - Likelihood = 50.2%

carp_continual_bacips_results_fall <- biomass.pcbacips(carp_biomass_continual_fall)
# STEP MODEL SELECTED - Likelihood = 50.3%



```

### segmented regression

#### annual

```{r}
aque_lm <- lm(delta_annual ~ time.model, data = aque_biomass_annual %>% filter(time.model > 0))
summary(aque_lm)
aque_seg_lm <- segmented(aque_lm)
summary(aque_seg_lm)
AIC(aque_lm, aque_seg_lm)
# very different, plot
aque_fit <- fitted(aque_seg_lm) %>% 
  enframe() %>% 
  rename(time.model = "name") %>% 
  mutate(time.model = as.numeric(time.model))
aque_seg_plot <- aque_biomass_annual %>% 
  left_join(., aque_fit, by = "time.model") %>% 
  ggplot(aes(x = time_since_end, y = delta_annual)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(aes(col = exp_dates)) +
  geom_smooth(aes(col = exp_dates), method = "lm") +
  geom_line(aes(y = value), size = 1, lty = 2, col = "blue") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 annual - AQUE") 
aque_seg_plot
# test for significant differences in slope between both segments
davies.test(aque_lm, seg.Z = ~time.model, k = 15)
# slopes in both segments are significantly different

napl_lm <- lm(delta_annual ~ time.model, data = napl_biomass_annual %>% filter(time.model > 0))
summary(napl_lm)
napl_seg_lm <- segmented(napl_lm)
AIC(napl_lm, napl_seg_lm)
# not very different, don't plot

ivee_lm <- lm(delta_annual ~ time.model, data = ivee_biomass_annual %>% filter(time.model > 0))
summary(ivee_lm)
ivee_seg_lm <- segmented(ivee_lm)
AIC(ivee_lm, ivee_seg_lm)
# seg is worse, don't plot

mohk_lm <- lm(delta_annual ~ time.model, data = mohk_biomass_annual %>% filter(time.model > 0))
summary(mohk_lm)
mohk_seg_lm <- segmented(mohk_lm)
AIC(mohk_lm, mohk_seg_lm)
# seg better, plot
mohk_fit <- fitted(mohk_seg_lm) %>% 
  enframe() %>% 
  rename(time.model = "name") %>% 
  mutate(time.model = as.numeric(time.model))
mohk_seg_plot <- mohk_biomass_annual %>% 
  left_join(., mohk_fit, by = "time.model") %>% 
  ggplot(aes(x = time_since_end, y = delta_annual)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(aes(col = exp_dates)) +
  geom_smooth(aes(col = exp_dates), method = "lm") +
  geom_line(aes(y = value), size = 1, lty = 2, col = "blue") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 annual - MOHK") 
mohk_seg_plot
# test for significant differences in slope between both segments
davies.test(mohk_lm, seg.Z = ~time.model, k = 15)
# slopes in both segments are not significantly different???????

carp_lm <- lm(delta_annual ~ time.model, data = carp_biomass_annual %>% filter(time.model > 0))
summary(carp_lm)
carp_seg_lm <- segmented(carp_lm)
AIC(carp_lm, carp_seg_lm)
# seg is better, plot
carp_fit <- fitted(carp_seg_lm) %>% 
  enframe() %>% 
  rename(time.model = "name") %>% 
  mutate(time.model = as.numeric(time.model))
carp_seg_plot <- carp_biomass_annual %>% 
  left_join(., carp_fit, by = "time.model") %>% 
  ggplot(aes(x = time_since_end, y = delta_annual)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(aes(col = exp_dates)) +
  geom_smooth(aes(col = exp_dates), method = "lm") +
  geom_line(aes(y = value), size = 1, lty = 2, col = "blue") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 annual - CARP") 
carp_seg_plot
# test for significant differences in slope between both segments
davies.test(carp_lm, seg.Z = ~time.model, k = 15)
# slopes in both segments are not significantly different???????
```

#### continual

```{r}
aque_lm <- lm(delta_continual ~ time.model, data = aque_biomass_continual %>% filter(time.model > 0))
summary(aque_lm)
aque_seg_lm <- segmented(aque_lm)
summary(aque_seg_lm)
AIC(aque_lm, aque_seg_lm)
# seg somewhat better, plot
aque_fit <- fitted(aque_seg_lm) %>% 
  enframe() %>% 
  rename(time.model = "name") %>% 
  mutate(time.model = as.numeric(time.model))
aque_seg_plot <- aque_biomass_continual %>% 
  left_join(., aque_fit, by = "time.model") %>% 
  ggplot(aes(x = time_since_end, y = delta_continual)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(aes(col = exp_dates)) +
  geom_smooth(aes(col = exp_dates), method = "lm") +
  geom_line(aes(y = value), size = 1, lty = 2, col = "blue") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 continual - AQUE")  
aque_seg_plot
# test for significant differences in slope between both segments
davies.test(aque_lm, seg.Z = ~time.model, k = 15)
# slopes in both segments are not significantly different

napl_lm <- lm(delta_continual ~ time.model, data = napl_biomass_continual %>% filter(time.model > 0))
summary(napl_lm)
napl_seg_lm <- segmented(napl_lm)
AIC(napl_lm, napl_seg_lm)
# seg is much better, plot
napl_fit <- fitted(napl_seg_lm) %>% 
  enframe() %>% 
  rename(time.model = "name") %>% 
  mutate(time.model = as.numeric(time.model))
napl_seg_plot <- napl_biomass_continual %>% 
  left_join(., napl_fit, by = "time.model") %>% 
  ggplot(aes(x = time_since_end, y = delta_continual)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(aes(col = exp_dates)) +
  geom_smooth(aes(col = exp_dates), method = "lm") +
  geom_line(aes(y = value), size = 1, lty = 2, col = "blue") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 continual - NAPL")   
napl_seg_plot
# test for significant differences in slope between both segments
davies.test(napl_lm, seg.Z = ~time.model, k = 15)
# significantly different slopes

mohk_lm <- lm(delta_continual ~ time.model, data = mohk_biomass_continual %>% filter(time.model > 0))
summary(mohk_lm)
mohk_seg_lm <- segmented(mohk_lm)
AIC(mohk_lm, mohk_seg_lm)
# seg is not better, skip

carp_lm <- lm(delta_continual ~ time.model, data = carp_biomass_continual %>% filter(time.model > 0))
summary(carp_lm)
carp_seg_lm <- segmented(carp_lm)
AIC(carp_lm, carp_seg_lm)
# seg is better, plot
carp_fit <- fitted(carp_seg_lm) %>% 
  enframe() %>% 
  rename(time.model = "name") %>% 
  mutate(time.model = as.numeric(time.model))
carp_seg_plot <- carp_biomass_continual %>% 
  left_join(., carp_fit, by = "time.model") %>% 
  ggplot(aes(x = time_since_end, y = delta_continual)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(aes(col = exp_dates)) +
  geom_smooth(aes(col = exp_dates), method = "lm") +
  geom_line(aes(y = value), size = 1, lty = 2, col = "blue") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 continual - CARP")  

carp_seg_plot
# test for significant differences in slope between both segments
davies.test(carp_lm, seg.Z = ~time.model, k = 15)
# significantly different slopes
```


### one sample t-test

As a reminder, the question is: are deltas in the "after" period significantly different from 0?

```{r}
aque_ttest <- t.test(delta_annual ~ 1, data = aque_biomass_annual %>% filter(exp_dates == "after"), alternative = "two.sided")
aque_ttest
# yes, mean = 101.68 - overshoot

napl_ttest <- t.test(delta_annual ~ 1, data = napl_biomass_annual %>% filter(exp_dates == "after"), alternative = "two.sided")
napl_ttest
# yes, mean = -72.29 - undershoot

ivee_ttest <- t.test(delta_annual ~ 1, data = ivee_biomass_annual %>% filter(exp_dates == "after"), alternative = "two.sided")
ivee_ttest
# yes, mean = 69.81 - overshoot

mohk_ttest <- t.test(delta_annual ~ 1, data = mohk_biomass_annual %>% filter(exp_dates == "after"), alternative = "less")
mohk_ttest
# no, mean = -166.79 - not significantly different from 0

carp_ttest <- t.test(delta_annual ~ 1, data = carp_biomass_annual %>% filter(exp_dates == "after"), alternative = "two.sided")
carp_ttest
# no, mean = 45.18 - not significantly different from 0
```


### Estimated slopes

#### All seasons
```{r}
aque_annual_slope <- aque_annual_bacips_results$linear.model.summary.coefficients[2, 1]
napl_annual_slope <- napl_annual_bacips_results$linear.model.summary.coefficients[2, 1]
ivee_annual_slope <- ivee_annual_bacips_results$linear.model.summary.coefficients[2, 1]
mohk_annual_slope <- mohk_annual_bacips_results$linear.model.summary.coefficients[2, 1]
carp_annual_slope <- carp_annual_bacips_results$linear.model.summary.coefficients[2, 1]

sites_annual_slope <- setNames(c(aque_annual_slope,
                                 napl_annual_slope,
                                 ivee_annual_slope,
                                 mohk_annual_slope,
                                 carp_annual_slope), LTE_sites) 

aque_annual_slope_pval <- aque_annual_bacips_results$linear.model.summary.coefficients[2, 4]
napl_annual_slope_pval <- napl_annual_bacips_results$linear.model.summary.coefficients[2, 4]
ivee_annual_slope_pval <- ivee_annual_bacips_results$linear.model.summary.coefficients[2, 4]
mohk_annual_slope_pval <- mohk_annual_bacips_results$linear.model.summary.coefficients[2, 4]
carp_annual_slope_pval <- carp_annual_bacips_results$linear.model.summary.coefficients[2, 4]

sites_annual_slope_pval <- setNames(c(aque_annual_slope_pval,
                                      napl_annual_slope_pval,
                                      ivee_annual_slope_pval,
                                      mohk_annual_slope_pval,
                                      carp_annual_slope_pval), LTE_sites)

aque_annual_model <- aque_annual_bacips_results$message
napl_annual_model <- napl_annual_bacips_results$message
ivee_annual_model <- ivee_annual_bacips_results$message
mohk_annual_model <- mohk_annual_bacips_results$message
carp_annual_model <- carp_annual_bacips_results$message

sites_annual_message <- c(aque_annual_model,
                          napl_annual_model,
                          ivee_annual_model,
                          mohk_annual_model,
                          carp_annual_model)

aque_annual_model_likelihood <- aque_annual_bacips_results$likelihood
napl_annual_model_likelihood <- napl_annual_bacips_results$likelihood
ivee_annual_model_likelihood <- ivee_annual_bacips_results$likelihood
mohk_annual_model_likelihood <- mohk_annual_bacips_results$likelihood
carp_annual_model_likelihood <- carp_annual_bacips_results$likelihood

sites_annual_model_likelihood <- c(aque_annual_model_likelihood,
                                   napl_annual_model_likelihood,
                                   ivee_annual_model_likelihood,
                                   mohk_annual_model_likelihood,
                                   carp_annual_model_likelihood)

aque_continual_slope <- aque_continual_bacips_results$linear.model.summary.coefficients[2, 1]
napl_continual_slope <- napl_continual_bacips_results$linear.model.summary.coefficients[2, 1]
mohk_continual_slope <- mohk_continual_bacips_results$linear.model.summary.coefficients[2, 1]
carp_continual_slope <- carp_continual_bacips_results$linear.model.summary.coefficients[2, 1]

sites_continual_slope <- setNames(c(aque_continual_slope,
                                    napl_continual_slope,
                                    mohk_continual_slope,
                                    carp_continual_slope), c("aque", "napl", "mohk", "carp"))

aque_continual_slope_pval <- aque_continual_bacips_results$linear.model.summary.coefficients[2, 4]
napl_continual_slope_pval <- napl_continual_bacips_results$linear.model.summary.coefficients[2, 4]
mohk_continual_slope_pval <- mohk_continual_bacips_results$linear.model.summary.coefficients[2, 4]
carp_continual_slope_pval <- carp_continual_bacips_results$linear.model.summary.coefficients[2, 4]

sites_continual_slope_pval <- setNames(c(aque_continual_slope_pval,
                                         napl_continual_slope_pval,
                                         mohk_continual_slope_pval,
                                         carp_continual_slope_pval), c("aque", "napl", "mohk", "carp"))


aque_continual_model <- aque_continual_bacips_results$message
napl_continual_model <- napl_continual_bacips_results$message
mohk_continual_model <- mohk_continual_bacips_results$message
carp_continual_model <- carp_continual_bacips_results$message

sites_continual_message <- setNames(c(aque_continual_model,
                                      napl_continual_model,
                                      mohk_continual_model,
                                      carp_continual_model), c("aque", "napl", "mohk", "carp"))

aque_continual_model_likelihood <- aque_continual_bacips_results$likelihood
napl_continual_model_likelihood <- napl_continual_bacips_results$likelihood
mohk_continual_model_likelihood <- mohk_continual_bacips_results$likelihood
carp_continual_model_likelihood <- carp_continual_bacips_results$likelihood

sites_continual_model_likelihood <- c(aque_continual_model_likelihood,
                                   napl_continual_model_likelihood,
                                   mohk_continual_model_likelihood,
                                   carp_continual_model_likelihood)
```

##### slopes of linear model

```{r}
sites_annual_slope_summary <- enframe(sites_annual_slope) %>% 
  rename(site = name, est_slope = value) %>% 
  cbind(sites_annual_slope_pval) %>% 
  rename(pval = sites_annual_slope_pval) %>% 
  cbind(sites_annual_message) %>% 
  rename(model_sel = sites_annual_message) %>% 
  cbind(sites_annual_model_likelihood) %>% 
  rename(likelihood = sites_annual_model_likelihood) %>% 
  cbind(sites_full) %>% 
  dplyr::select(sites_full, est_slope, pval, model_sel, likelihood) %>% 
  mutate(across(c(est_slope, pval), ~ round(., digits = 3))) %>% 
  gt() %>% 
  cols_label(
    sites_full = "Site",
    est_slope = "Linear slope \n (estimated)",
    pval = "p-value",
    model_sel = "Selected model",
    likelihood = "Likelihood"
  ) %>% 
  tab_header(
    title = "Annual removal slopes: all seasons"
  ) 

sites_annual_slope_summary %>% 
  gtsave(paste("annual_removal_slopes-", todays_date, ".png", sep = ""), path = here::here("tables"))

sites_continual_slope_summary <- enframe(sites_continual_slope) %>% 
  rename(site = name, est_slope = value) %>% 
  cbind(sites_continual_slope_pval) %>% 
  rename(pval = sites_continual_slope_pval) %>% 
  cbind(sites_continual_message) %>% 
  rename(model_sel = sites_continual_message) %>% 
  cbind(sites_continual_model_likelihood) %>% 
  rename(likelihood = sites_continual_model_likelihood) %>% 
  cbind(sites_continual_full) %>% 
  dplyr::select(sites_continual_full, est_slope, pval, model_sel, likelihood) %>% 
  mutate(across(c(est_slope, pval), ~ round(., digits = 3))) %>% 
  gt() %>% 
  cols_label(
    sites_continual_full = "Site",
    est_slope = "Linear slope \n (estimated)",
    pval = "p-value",
    model_sel = "Selected model",
    likelihood = "Likelihood"
  ) %>% 
  tab_header(
    title = "Continual removal slopes: all seasons"
  ) 

sites_continual_slope_summary %>% 
  gtsave(paste("continual_removal_slopes-", todays_date, ".png", sep = ""), path = here::here("tables"))
```

##### models selected
```{r}
sites_annual_summary <- enframe(sites_annual_slope) %>% 
  rename(site = name, est_slope = value) %>% 
  cbind(sites_annual_slope_pval) %>% 
  rename(pval = sites_annual_slope_pval) %>% 
  cbind(sites_annual_message) %>% 
  rename(model_sel = sites_annual_message) %>% 
  cbind(sites_annual_model_likelihood) %>% 
  rename(likelihood = sites_annual_model_likelihood) %>% 
  cbind(sites_full) %>% 
  dplyr::select(sites_full, model_sel, likelihood) %>%  
  gt() %>% 
  cols_label(
    sites_full = "Site",
    model_sel = "Selected model",
    likelihood = "Likelihood"
  ) %>% 
  tab_header(
    title = "Annual removal model selections: all seasons"
  ) 

sites_annual_summary %>% 
  gtsave(paste("annual_removal_models-", todays_date, ".png", sep = ""), path = here::here("tables"))

sites_continual_summary <- enframe(sites_continual_slope) %>% 
  rename(site = name, est_slope = value) %>% 
  cbind(sites_continual_slope_pval) %>% 
  rename(pval = sites_continual_slope_pval) %>% 
  cbind(sites_continual_message) %>% 
  rename(model_sel = sites_continual_message) %>% 
  cbind(sites_continual_model_likelihood) %>% 
  rename(likelihood = sites_continual_model_likelihood) %>% 
  cbind(sites_continual_full) %>% 
  dplyr::select(sites_continual_full, model_sel, likelihood) %>% 
  gt() %>% 
  cols_label(
    sites_continual_full = "Site",
    model_sel = "Selected model",
    likelihood = "Likelihood"
  ) %>% 
  tab_header(
    title = "Continual removal model selections: all seasons"
  ) 

sites_continual_summary %>% 
  gtsave(paste("continual_removal_models-", todays_date, ".png", sep = ""), path = here::here("tables"))
```


#### Summer only

```{r}
aque_annual_slope <- aque_annual_bacips_results_summer$linear.model.summary.coefficients[2, 1]
napl_annual_slope <- napl_annual_bacips_results_summer$linear.model.summary.coefficients[2, 1]
ivee_annual_slope <- ivee_annual_bacips_results_summer$linear.model.summary.coefficients[2, 1]
mohk_annual_slope <- mohk_annual_bacips_results_summer$linear.model.summary.coefficients[2, 1]
carp_annual_slope <- carp_annual_bacips_results_summer$linear.model.summary.coefficients[2, 1]

sites_annual_slope <- setNames(c(aque_annual_slope,
                                 napl_annual_slope,
                                 ivee_annual_slope,
                                 mohk_annual_slope,
                                 carp_annual_slope), LTE_sites) 

aque_annual_slope_pval <- aque_annual_bacips_results_summer$linear.model.summary.coefficients[2, 4]
napl_annual_slope_pval <- napl_annual_bacips_results_summer$linear.model.summary.coefficients[2, 4]
ivee_annual_slope_pval <- ivee_annual_bacips_results_summer$linear.model.summary.coefficients[2, 4]
mohk_annual_slope_pval <- mohk_annual_bacips_results_summer$linear.model.summary.coefficients[2, 4]
carp_annual_slope_pval <- carp_annual_bacips_results_summer$linear.model.summary.coefficients[2, 4]

sites_annual_slope_pval <- setNames(c(aque_annual_slope_pval,
                                      napl_annual_slope_pval,
                                      ivee_annual_slope_pval,
                                      mohk_annual_slope_pval,
                                      carp_annual_slope_pval), LTE_sites)

aque_annual_model <- aque_annual_bacips_results_summer$message
napl_annual_model <- napl_annual_bacips_results_summer$message
ivee_annual_model <- ivee_annual_bacips_results_summer$message
mohk_annual_model <- mohk_annual_bacips_results_summer$message
carp_annual_model <- carp_annual_bacips_results_summer$message

sites_annual_message <- c(aque_annual_model,
                          napl_annual_model,
                          ivee_annual_model,
                          mohk_annual_model,
                          carp_annual_model)

aque_annual_model_likelihood <- aque_annual_bacips_results_summer$likelihood
napl_annual_model_likelihood <- napl_annual_bacips_results_summer$likelihood
ivee_annual_model_likelihood <- ivee_annual_bacips_results_summer$likelihood
mohk_annual_model_likelihood <- mohk_annual_bacips_results_summer$likelihood
carp_annual_model_likelihood <- carp_annual_bacips_results_summer$likelihood

sites_annual_model_likelihood <- c(aque_annual_model_likelihood,
                                   napl_annual_model_likelihood,
                                   ivee_annual_model_likelihood,
                                   mohk_annual_model_likelihood,
                                   carp_annual_model_likelihood)

aque_continual_slope <- aque_continual_bacips_results_summer$linear.model.summary.coefficients[2, 1]
napl_continual_slope <- napl_continual_bacips_results_summer$linear.model.summary.coefficients[2, 1]
mohk_continual_slope <- mohk_continual_bacips_results_summer$linear.model.summary.coefficients[2, 1]
carp_continual_slope <- carp_continual_bacips_results_summer$linear.model.summary.coefficients[2, 1]

sites_continual_slope <- setNames(c(aque_continual_slope,
                                    napl_continual_slope,
                                    mohk_continual_slope,
                                    carp_continual_slope), c("aque", "napl", "mohk", "carp"))

aque_continual_slope_pval <- aque_continual_bacips_results_summer$linear.model.summary.coefficients[2, 4]
napl_continual_slope_pval <- napl_continual_bacips_results_summer$linear.model.summary.coefficients[2, 4]
mohk_continual_slope_pval <- mohk_continual_bacips_results_summer$linear.model.summary.coefficients[2, 4]
carp_continual_slope_pval <- carp_continual_bacips_results_summer$linear.model.summary.coefficients[2, 4]

sites_continual_slope_pval <- setNames(c(aque_continual_slope_pval,
                                         napl_continual_slope_pval,
                                         mohk_continual_slope_pval,
                                         carp_continual_slope_pval), c("aque", "napl", "mohk", "carp"))


aque_continual_model <- aque_continual_bacips_results_summer$message
napl_continual_model <- napl_continual_bacips_results_summer$message
mohk_continual_model <- mohk_continual_bacips_results_summer$message
carp_continual_model <- carp_continual_bacips_results_summer$message

sites_continual_message <- setNames(c(aque_continual_model,
                                      napl_continual_model,
                                      mohk_continual_model,
                                      carp_continual_model), c("aque", "napl", "mohk", "carp"))

aque_continual_model_likelihood <- aque_continual_bacips_results_summer$likelihood
napl_continual_model_likelihood <- napl_continual_bacips_results_summer$likelihood
mohk_continual_model_likelihood <- mohk_continual_bacips_results_summer$likelihood
carp_continual_model_likelihood <- carp_continual_bacips_results_summer$likelihood

sites_continual_model_likelihood <- c(aque_continual_model_likelihood,
                                   napl_continual_model_likelihood,
                                   mohk_continual_model_likelihood,
                                   carp_continual_model_likelihood)
```

```{r}
sites_annual_slope_summary <- enframe(sites_annual_slope) %>% 
  rename(site = name, est_slope = value) %>% 
  cbind(sites_annual_slope_pval) %>% 
  rename(pval = sites_annual_slope_pval) %>% 
  cbind(sites_annual_message) %>% 
  rename(model_sel = sites_annual_message) %>% 
  cbind(sites_annual_model_likelihood) %>% 
  rename(likelihood = sites_annual_model_likelihood) %>% 
  cbind(sites_full) %>% 
  select(sites_full, est_slope, pval, model_sel, likelihood) %>% 
  mutate(across(c(est_slope, pval), ~ round(., digits = 3))) %>% 
  gt() %>% 
  cols_label(
    sites_full = "Site",
    est_slope = "Linear slope \n (estimated)",
    pval = "p-value",
    model_sel = "Selected model",
    likelihood = "Likelihood"
  ) %>% 
  tab_header(
    title = "Annual removal slopes: summer"
  ) 

sites_annual_slope_summary %>% 
  gtsave(paste("annual_removal_slopes-summer-", todays_date, ".png", sep = ""), path = here::here("tables"))

sites_continual_slope_summary <- enframe(sites_continual_slope) %>% 
  rename(site = name, est_slope = value) %>% 
  cbind(sites_continual_slope_pval) %>% 
  rename(pval = sites_continual_slope_pval) %>% 
  cbind(sites_continual_message) %>% 
  rename(model_sel = sites_continual_message) %>% 
  cbind(sites_continual_model_likelihood) %>% 
  rename(likelihood = sites_continual_model_likelihood) %>% 
  cbind(sites_continual_full) %>% 
  select(sites_continual_full, est_slope, pval, model_sel, likelihood) %>% 
  mutate(across(c(est_slope, pval), ~ round(., digits = 3))) %>% 
  gt() %>% 
  cols_label(
    sites_continual_full = "Site",
    est_slope = "Linear slope \n (estimated)",
    pval = "p-value",
    model_sel = "Selected model",
    likelihood = "Likelihood"
  ) %>% 
  tab_header(
    title = "Continual removal slopes: summer"
  ) 

sites_continual_slope_summary %>% 
  gtsave(paste("continual_removal_slopes_summer-", todays_date, ".png", sep = ""), path = here::here("tables"))

```

#### Fall only

```{r}
aque_annual_slope <- aque_annual_bacips_results_fall$linear.model.summary.coefficients[2, 1]
napl_annual_slope <- napl_annual_bacips_results_fall$linear.model.summary.coefficients[2, 1]
ivee_annual_slope <- ivee_annual_bacips_results_fall$linear.model.summary.coefficients[2, 1]
mohk_annual_slope <- mohk_annual_bacips_results_fall$linear.model.summary.coefficients[2, 1]
carp_annual_slope <- carp_annual_bacips_results_fall$linear.model.summary.coefficients[2, 1]

sites_annual_slope <- setNames(c(aque_annual_slope,
                                 napl_annual_slope,
                                 ivee_annual_slope,
                                 mohk_annual_slope,
                                 carp_annual_slope), LTE_sites) 

aque_annual_slope_pval <- aque_annual_bacips_results_fall$linear.model.summary.coefficients[2, 4]
napl_annual_slope_pval <- napl_annual_bacips_results_fall$linear.model.summary.coefficients[2, 4]
ivee_annual_slope_pval <- ivee_annual_bacips_results_fall$linear.model.summary.coefficients[2, 4]
mohk_annual_slope_pval <- mohk_annual_bacips_results_fall$linear.model.summary.coefficients[2, 4]
carp_annual_slope_pval <- carp_annual_bacips_results_fall$linear.model.summary.coefficients[2, 4]

sites_annual_slope_pval <- setNames(c(aque_annual_slope_pval,
                                      napl_annual_slope_pval,
                                      ivee_annual_slope_pval,
                                      mohk_annual_slope_pval,
                                      carp_annual_slope_pval), LTE_sites)

aque_annual_model <- aque_annual_bacips_results_fall$message
napl_annual_model <- napl_annual_bacips_results_fall$message
ivee_annual_model <- ivee_annual_bacips_results_fall$message
mohk_annual_model <- mohk_annual_bacips_results_fall$message
carp_annual_model <- carp_annual_bacips_results_fall$message

sites_annual_message <- c(aque_annual_model,
                          napl_annual_model,
                          ivee_annual_model,
                          mohk_annual_model,
                          carp_annual_model)

aque_annual_model_likelihood <- aque_annual_bacips_results_fall$likelihood
napl_annual_model_likelihood <- napl_annual_bacips_results_fall$likelihood
ivee_annual_model_likelihood <- ivee_annual_bacips_results_fall$likelihood
mohk_annual_model_likelihood <- mohk_annual_bacips_results_fall$likelihood
carp_annual_model_likelihood <- carp_annual_bacips_results_fall$likelihood

sites_annual_model_likelihood <- c(aque_annual_model_likelihood,
                                   napl_annual_model_likelihood,
                                   ivee_annual_model_likelihood,
                                   mohk_annual_model_likelihood,
                                   carp_annual_model_likelihood)

aque_continual_slope <- aque_continual_bacips_results_fall$linear.model.summary.coefficients[2, 1]
napl_continual_slope <- napl_continual_bacips_results_fall$linear.model.summary.coefficients[2, 1]
mohk_continual_slope <- mohk_continual_bacips_results_fall$linear.model.summary.coefficients[2, 1]
carp_continual_slope <- carp_continual_bacips_results_fall$linear.model.summary.coefficients[2, 1]

sites_continual_slope <- setNames(c(aque_continual_slope,
                                    napl_continual_slope,
                                    mohk_continual_slope,
                                    carp_continual_slope), c("aque", "napl", "mohk", "carp"))

aque_continual_slope_pval <- aque_continual_bacips_results_fall$linear.model.summary.coefficients[2, 4]
napl_continual_slope_pval <- napl_continual_bacips_results_fall$linear.model.summary.coefficients[2, 4]
mohk_continual_slope_pval <- mohk_continual_bacips_results_fall$linear.model.summary.coefficients[2, 4]
carp_continual_slope_pval <- carp_continual_bacips_results_fall$linear.model.summary.coefficients[2, 4]

sites_continual_slope_pval <- setNames(c(aque_continual_slope_pval,
                                         napl_continual_slope_pval,
                                         mohk_continual_slope_pval,
                                         carp_continual_slope_pval), c("aque", "napl", "mohk", "carp"))


aque_continual_model <- aque_continual_bacips_results_fall$message
napl_continual_model <- napl_continual_bacips_results_fall$message
mohk_continual_model <- mohk_continual_bacips_results_fall$message
carp_continual_model <- carp_continual_bacips_results_fall$message

sites_continual_message <- setNames(c(aque_continual_model,
                                      napl_continual_model,
                                      mohk_continual_model,
                                      carp_continual_model), c("aque", "napl", "mohk", "carp"))

aque_continual_model_likelihood <- aque_continual_bacips_results_fall$likelihood
napl_continual_model_likelihood <- napl_continual_bacips_results_fall$likelihood
mohk_continual_model_likelihood <- mohk_continual_bacips_results_fall$likelihood
carp_continual_model_likelihood <- carp_continual_bacips_results_fall$likelihood

sites_continual_model_likelihood <- c(aque_continual_model_likelihood,
                                   napl_continual_model_likelihood,
                                   mohk_continual_model_likelihood,
                                   carp_continual_model_likelihood)
```

```{r}
sites_annual_slope_summary <- enframe(sites_annual_slope) %>% 
  rename(site = name, est_slope = value) %>% 
  cbind(sites_annual_slope_pval) %>% 
  rename(pval = sites_annual_slope_pval) %>% 
  cbind(sites_annual_message) %>% 
  rename(model_sel = sites_annual_message) %>% 
  cbind(sites_annual_model_likelihood) %>% 
  rename(likelihood = sites_annual_model_likelihood) %>% 
  cbind(sites_full) %>% 
  select(sites_full, est_slope, pval, model_sel, likelihood) %>% 
  mutate(across(c(est_slope, pval), ~ round(., digits = 3))) %>% 
  gt() %>% 
  cols_label(
    sites_full = "Site",
    est_slope = "Linear slope \n (estimated)",
    pval = "p-value",
    model_sel = "Selected model",
    likelihood = "Likelihood"
  ) %>% 
  tab_header(
    title = "Annual removal slopes: fall"
  ) 

sites_annual_slope_summary %>% 
  gtsave(paste("annual_removal_slopes-fall-", todays_date, ".png", sep = ""), path = here::here("tables"))

sites_continual_slope_summary <- enframe(sites_continual_slope) %>% 
  rename(site = name, est_slope = value) %>% 
  cbind(sites_continual_slope_pval) %>% 
  rename(pval = sites_continual_slope_pval) %>% 
  cbind(sites_continual_message) %>% 
  rename(model_sel = sites_continual_message) %>% 
  cbind(sites_continual_model_likelihood) %>% 
  rename(likelihood = sites_continual_model_likelihood) %>% 
  cbind(sites_continual_full) %>% 
  select(sites_continual_full, est_slope, pval, model_sel, likelihood) %>% 
  mutate(across(c(est_slope, pval), ~ round(., digits = 3))) %>% 
  gt() %>% 
  cols_label(
    sites_continual_full = "Site",
    est_slope = "Linear slope \n (estimated)",
    pval = "p-value",
    model_sel = "Selected model",
    likelihood = "Likelihood"
  ) %>% 
  tab_header(
    title = "Continual removal slopes: fall"
  ) 

sites_continual_slope_summary %>% 
  gtsave(paste("continual_removal_slopes_fall-", todays_date, ".png", sep = ""), path = here::here("tables"))

```

### All sites

#### test

Testing out code to get total fronds for each sampling date across sites starting with 2 sites: aque and napl. Each observation in the output should have a sampling year, total fronds in the annual, total fronds in the continual, and total fronds in the control.

```{r}
test_annual <- delta_fronds %>% 
  filter(site == "aque" | site == "napl") %>% 
  arrange(year, site) %>% 
  group_by(year, season) %>% 
  mutate(total_annual_all = sum(annual, na.rm = TRUE),
         total_continual_all = sum(continual, na.rm = TRUE),
         total_control_all = sum(control, na.rm = TRUE)) %>% 
  ungroup() %>% 
  select(year, month, exp_dates, total_annual_all:total_control_all) %>% 
  unique() %>% 
  mutate(delta_annual_all = total_annual_all - total_control_all,
         delta_continual_all = total_continual_all - total_control_all)

ggplot(test_annual, aes(x = year)) +
  geom_line(aes(y = delta_annual_all), col = annual_col) +
  geom_point(aes(y = delta_annual_all), col = annual_col, shape = annual_shape) +
  geom_line(aes(y = delta_continual_all), col = continual_col) +
  geom_point(aes(y = delta_continual_all), col = continual_col, shape = continual_shape) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  labs(x = "Year", y = "delta kelp fronds (removal - control)")
```

## Biomass by season figure

x-axis: time from winter to fall  
y-axis: kelp biomass  
lines: colored by sampling date and year  

Going to try with aque first:
```{r}
aque_test <- kelp_biomass %>% 
  filter(site == "aque" & year %in% c(2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
  unite("color", treatment, year, sep = "_", remove = FALSE) %>% 
  # make a new column for the year label lol i am a clown
  mutate(year_label = case_when(
    season == "winter" ~ as.character(year),
    TRUE ~ ""
  )) %>% 
  ggplot(aes(x = season, y = total_wm_gm2, group = color)) +
  geom_point(aes(color = color)) +
  geom_line(aes(color = color)) +
  geom_text_repel(aes(label = year_label, color = color)) +
  theme(legend.position = "none") +
  facet_wrap(~ treatment + exp_dates, nrow = 3, ncol = 2)


aque_test
```

Ok great. Going to do the rest now:

```{r}
biomass_by_season <- function(site_choice) {
  plot_title <- pluck(sites_full, site_choice)
  
  kelp_biomass %>% 
    # filter(site == site_choice) %>% 
    unite("color", treatment, year, sep = "_", remove = FALSE) %>% 
    # make a new column for the year label
    mutate(year_label = case_when(
      season == "winter" ~ as.character(year),
      TRUE ~ ""
    )) %>%
    mutate(season = fct_relevel(season, c("winter", "spring", "summer", "fall"))) %>% 
    ggplot(aes(x = season, y = wm_gm2, group = color)) +
    # stat summary for point and SE for mean biomass during and after with line
    stat_summary(aes(group = season, color = site), fun = mean, geom = "line", size = 1, alpha = 0.8) +
    stat_summary(aes(group = season, color = site), fun = mean, geom = "point", size = 4) +
    stat_summary(aes(group = season, color = site), fun.data = mean_se, geom = "errorbar", alpha = 0.8, width = 0.2) +
  # geom_point(aes(color = year)) +
  #   geom_line(aes(color = year)) +
    # geom_text_repel(aes(label = year_label, color = year),
    #                 nudge_x = 1.5, nudge_y = 0.1,
    #                 segment.curvature = -1e-20, point.padding = 0.2,
    #                 force_pull = 10) +
    theme_bw() +
    theme(legend.position = "none",
          plot.title = element_text(size = 20),
          strip.background = element_rect(fill = "#FFFFFF")) +
    facet_wrap(~ treatment + exp_dates, nrow = 3, ncol = 2) +
    labs(x = "Season", y = "Total biomass (wet g/m2)",
         title = plot_title)
}

aque_biomass_season <- biomass_by_season("aque")
napl_biomass_season <- biomass_by_season("napl")
ivee_biomass_season <- biomass_by_season("ivee")
mohk_biomass_season <- biomass_by_season("mohk")
carp_biomass_season <- biomass_by_season("carp")

delta_annual %>% 
  filter(site == "carp") %>% 
  mutate(season = case_when(
    quarter == "Q2" ~ "spring",
    quarter == "Q3" ~ "summer",
    quarter == "Q4" ~ "fall",
    quarter == "Q1" ~ "winter"
  )) %>% 
  mutate(season = fct_relevel(season, "spring", "summer", "fall", "winter")) %>% 
  filter(exp_dates == "during") %>% 
  mutate(quarter = fct_relevel(quarter, "Q2", "Q3", "Q4", "Q1")) %>% 
  mutate(kelp_year = as.factor(kelp_year)) %>% 
  ggplot(aes(x = season, y = annual)) +
  stat_summary(aes(color = kelp_year, group = kelp_year), fun.data = mean_se, geom = "errorbar", alpha = 0.5, width = 0.2) +
  # geom_point(aes(shape = site, color = kelp_year), size = 2) +
  stat_summary(aes(color = kelp_year, group = kelp_year), fun = mean, geom = "line", size = 2) +
  scale_color_manual(values = c("#BBD1FA", "#A2B9E4", "#89A1CE", "#7089B8",
                                "#5771A2", "#3E598C", "#254176", "#0D2A61", "darkblue", "navy", "black")) +
  theme_bw() +
  labs(x = "Season",
       y = "Kelp biomass",
       caption = "carp") +
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        panel.grid = element_blank())
  # ggsave(here::here("figures", paste("biomass-by-season_carp_", todays_date, ".jpg", sep = "")),  
  #        height = 10, width = 8, dpi = 150)

# ggsave(here::here("figures", "biomass-by-season_aque_2022-02-08.jpg"), aque_biomass_season, height = 10, width = 8, dpi = 200)

# ggsave(here::here("figures", "biomass-by-season_napl_2022-02-08.jpg"), napl_biomass_season, height = 10, width = 8, dpi = 200)

# ggsave(here::here("figures", "biomass-by-season_ivee_2022-02-08.jpg"), ivee_biomass_season, height = 10, width = 8, dpi = 200)

# ggsave(here::here("figures", "biomass-by-season_mohk_2022-02-08.jpg"), mohk_biomass_season, height = 10, width = 8, dpi = 200)

# ggsave(here::here("figures", "biomass-by-season_carp_2022-02-08.jpg"), carp_biomass_season, height = 10, width = 8, dpi = 200)
```

```{r}
annual_removal_biomass_by_season <- kelp_biomass %>% 
  filter(treatment == "annual") %>% 
  unite("color", treatment, year, sep = "_", remove = FALSE) %>% 
  # make a new column for the year label
  mutate(year_label = case_when(
    season == "winter" ~ as.character(year),
    TRUE ~ ""
  )) %>% 
  ggplot(aes(x = season, y = wm_gm2)) +
  # stat summary for point and SE for mean biomass during and after with line
  stat_summary(aes(group = site, color = site), fun = mean, geom = "line", size = 1, alpha = 0.8) +
  stat_summary(aes(group = site, color = site), fun = mean, geom = "point", size = 4) +
  stat_summary(aes(group = site, color = site), fun.data = mean_se, geom = "errorbar", alpha = 0.8, width = 0.2) +
  scale_color_manual(values = site_palette) +
  theme_bw() +
  theme(plot.title = element_text(size = 40),
        strip.background = element_rect(fill = "#FFFFFF"),
        strip.text = element_text(size = 18)) +
  facet_wrap(~ exp_dates) +
  labs(x = "Season", y = "Mean biomass (wet g/m2)",
       title = "Annual removal biomass") 

  # ggsave(here::here("figures", "annual_biomass_timeseries.jpg"), annual_removal_biomass_by_season, width = 14, height = 8, dpi = 300)
```

```{r}
biomass_by_season_all <- kelp_biomass %>% 
  unite("color", treatment, year, sep = "_", remove = FALSE) %>% 
  # make a new column for the year label
  mutate(year_label = case_when(
    season == "winter" ~ as.character(year),
    TRUE ~ ""
  )) %>%
  mutate(season = fct_relevel(season, c("winter", "spring", "summer", "fall"))) %>% 
  ggplot(aes(x = season, y = wm_gm2, group = site)) +
  # stat summary for point and SE for mean biomass during and after with line
  stat_summary(aes(group = site, color = site), fun = mean, geom = "line", size = 1, alpha = 0.8) +
  stat_summary(aes(group = site, color = site), fun = mean, geom = "point", size = 4) +
  stat_summary(aes(group = site, color = site), fun.data = mean_se, geom = "errorbar", alpha = 0.8, width = 0.2) +
  scale_color_manual(values = site_palette) +
  theme_bw() +
  theme(plot.title = element_text(size = 20),
        strip.background = element_rect(fill = "#FFFFFF"),
        strip.text = element_text(size = 14),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 12)) +
  facet_wrap(~ treatment + exp_dates, nrow = 3, ncol = 2) +
  labs(x = "Season", y = "Mean biomass (wet g/m2)",
       title = "Mean kelp biomass within season across sampling years")

# ggsave(here::here("figures", "annual_biomass_timeseries.jpg"), biomass_by_season_all, width = 11, height = 12, dpi = 300)
```


## Fall biomass figure

x-axis: time  
y-axis: biomass  
only including fall sampling dates

```{r}
kelp_biomass_fall <- kelp_biomass %>% 
  filter(season == "fall") %>% 
  ggplot(aes(x = date, y = wm_gm2)) +
  geom_line(aes(color = treatment), size = 1) +
  geom_point(aes(color = treatment, shape = treatment), size = 3) +
  scale_color_manual(values = color_palette) +
  scale_shape_manual(values = shape_palette) +
  theme_bw() +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        title = element_text(size = 20),
        legend.text = element_text(size = 16)) +
  facet_wrap(~site) +
  labs(x = "Sampling date", y = "Total biomass (wet mass/gm2)",
       title = "Fall kelp biomass")

kelp_biomass_summer <- kelp_biomass %>% 
  filter(season == "summer") %>% 
  ggplot(aes(x = date, y = wm_gm2)) +
  geom_line(aes(color = treatment), size = 1) +
  geom_point(aes(color = treatment, shape = treatment), size = 3) +
  scale_color_manual(values = color_palette) +
  scale_shape_manual(values = shape_palette) +
  theme_bw() +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        title = element_text(size = 20),
        legend.text = element_text(size = 16)) +
  facet_wrap(~site) +
  labs(x = "Sampling date", y = "Total biomass (wet mass/gm2)",
       title = "Summer kelp biomass")

kelp_biomass_fall
kelp_biomass_summer

# ggsave(here::here("figures/timeseries", paste("kelp-biomass_summer_", todays_date, ".jpg", sep = "")), kelp_biomass_summer)

# ggsave(here::here("figures/timeseries", paste("kelp-biomass_fall_", todays_date, ".jpg", sep = "")), kelp_biomass_fall)
```

## Kelp "recovery" by productivity

Plot with "productivity" on x-axis (CARP, AQUE, NAPL, MOHK, IVEE) and time to recovery (delta = 0) on y axis.

```{r}
df <- delta_biomass %>% 
  filter(site == "mohk" & exp_dates == "after") %>% 
  group_by(site) %>% 
  mutate(time_to_zero = row_number())
  
```

## Removal kelp as a function of control

### test

What I want is to have a plot where kelp biomass in the control is the x-axis, and kelp biomass in the removal is the y-axis, and there is a 1:1 line as the diagonal, and each point is connected by an arrow indicating time across sampling dates.

```{r}
delta_biomass %>% 
  filter(site == "aque") %>% 
  ggplot(aes(x = control, y = annual)) +
  geom_text(aes(col = exp_dates, label = date)) +
  geom_abline(slope = 1, intercept = 0) +
  coord_cartesian()
```

## Ratio of kelp in removal:control plots

Connell et al. 1997:  
 - damage: 100 x (difference between abundance in census before with that just after disturbance)/(abundance in census just before disturbance)
 - short term rate of recovery: 100 x (change in abundance between first two censuses)/(damage during disturbance), which is then standardized to 2 year period by "linear interpolation of period between two post-storm censuses"  
 - extent of recovery: 100 x (highest abundance in period before next disturbance)/(damage during first disturbance)  
 
So, for kelp:
- impact of removal: 100 x (difference in biomass in control - removal)/(biomass in control)
- rate of recovery: 100 x (change in abundance between end of experiment and sampling date)/(impact of removal)  
- extent of recovery: 100 x (highest abundance in period after disturbance)/(impact of removal)

```{r}
df <- delta_biomass %>% 
  filter(site == "aque") %>% 
  mutate(delta_annual = control - annual,
         delta_continual = control - continual, 
         impact_annual = round((delta_annual/control), 4),
         impact_continual = round((delta_continual/control), 4)) %>% 
  filter(impact_annual > -Inf)

ggplot(df) +
  geom_line(aes(x = date, y = impact_annual), col = "red") +
  # geom_line(aes(x = date, y = impact_continual), col = "blue") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
  annotate("text", x = as.Date("2018-01-01"), y = 10, label = "more kelp in control", size = 3) +
  annotate("text", x = as.Date("2018-01-01"), y = -10, label = "more kelp in removal", size = 3) +
  theme_bw() +
  labs(x = "Date", y = "Removal impact [(control-annual)/control]",
       title = "Removal impact - AQUE")

ggplot(df, aes(x = control, y = delta_annual)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
  geom_smooth(method = "lm", aes(color = exp_dates)) +
  theme_bw() +
  labs(x = "Control kelp biomass", y = "Biomass difference (control - removal)",
       title = "AQUE - delta biomass as a function of control kelp biomass") +
  annotate("text", x = 6000, y = 200, label = "more kelp in control", size = 3) +
  annotate("text", x = 6000, y = -200, label = "more kelp in removal", size = 3) 

ggplot(df %>% filter(impact_annual > -200), aes(x = control, y = impact_annual)) +
  geom_point() +
  # geom_point(data = df %>% filter(impact_annual < -500), aes(x = control, y = impact_annual), col = "red") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
  geom_smooth(method = "lm", aes(color = exp_dates)) +
  theme_bw() +
    labs(x = "Control kelp biomass", y = "Removal impact [(control-annual)/control]",
       title = "AQUE - removal impact as a function of control kelp biomass") +
  annotate("text", x = 6000, y = 50, label = "more kelp in control", size = 3) +
  annotate("text", x = 6000, y = -50, label = "more kelp in removal", size = 3) 
```

Or, could try impact/rate/recovery with means...  

Just as a note, there probably needs to be two different data frames? Or maybe this can be done in vectors... regardless, maybe it could be a matrix that is 5 rows long, with columns for mean biomass annual during, mean biomass continual during... then deltas would be biomass

```{r}

# - impact of removal: 100 x (difference in biomass in control - removal)/(biomass in control)
# issues: when removal = 0 --> solution: change 0 to 0.000001? or some very small number?
# - rate of recovery: 100 x (change in abundance between end of experiment and sampling date)/(impact of removal)  
# - extent of recovery: 100 x (highest abundance in period after disturbance)/(impact of removal)

# Connell 1997: extent of recovery: ratio of increase to the amount of decline
# e.g. if cover fell from 75% to 25%, then rose to 55%, then degree of recovery = 60% (rise 30%/fall 50%)


recovery_df <- biomass %>% 
  filter(sp_code == "MAPY") %>% 
  select(-sp_code) %>% 
  # # make a new column for after dates
  after_dates_column() %>% 
  # make a new column for during and after and set factor levels
  exp_dates_column() %>% 
  # select(site, treatment, date, exp_dates, wm_gm2) %>% 
  group_by(exp_dates, site, treatment) %>% 
  summarize(mean_biomass = mean(wm_gm2, na.rm = TRUE)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = c(treatment, exp_dates), values_from = mean_biomass) %>% 
  # difference between control and removal during and after experiment ends
  mutate(during_delta_annual = control_during - annual_during,
         during_delta_continual = control_during - continual_during,
         # "rise" is the increase after the experiment ends (difference between after and during)
         both_rise_annual = annual_after - annual_during,
         both_rise_continual = continual_after - continual_during,
         # impact is the ratio of delta:control biomass
         both_impact_annual = (during_delta_annual/control_during)*100,
         both_impact_continual = (during_delta_continual/control_during)*100,
         # rate of recovery is the ratio of rise:impact
         both_rate_annual = both_rise_annual/both_impact_annual,
         both_rate_continual = both_rise_continual/both_impact_continual,
         # extent is the ratio of rise:delta
         both_extent_annual = both_rise_annual/during_delta_annual,
         both_extent_continual = both_rise_continual/during_delta_continual,
         after_delta_annual = control_after - annual_after,
         after_delta_continual = control_after - continual_after
  ) %>% 
  # new column with full site names
  mutate(site_full = case_when(
    site == "aque" ~ aque_full,
    site == "napl" ~ napl_full,
    site == "ivee" ~ ivee_full,
    site == "mohk" ~ mohk_full,
    site == "carp" ~ carp_full
  )) %>% 
  pivot_longer(cols = 8:19, names_to = "calc", values_to = "value") %>% 
  separate(col = calc, into = c("exp_dates", "calc", "treatment")) %>% 
  select(site_full, exp_dates, calc, treatment, value) %>% 
  mutate(site_full = fct_relevel(site_full, aque_full, napl_full, ivee_full, mohk_full, carp_full)) 

aque_comparison_biomass
napl_comparison_biomass
ivee_comparison_biomass
mohk_comparison_biomass
carp_comparison_biomass

impact_plot <- ggplot(recovery_df %>% filter(calc == "impact"), aes(x = site_full, y = value)) +
  geom_col(aes(fill = treatment), position = "dodge") +
  scale_fill_manual(values = c(annual_col, continual_col)) +
  geom_hline(yintercept = 0, lty = 2) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  theme_bw() +
  labs(x = "Site", y = "Mean kelp biomass impact [(\u0394 control - removal)/control]",
       title = "Impact of removal during experiment") +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        title = element_text(size = 18),
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 16))
impact_plot
# ggsave(here::here("figures/recovery-metrics", paste("impact_", todays_date, ".jpg", sep = "")), impact_plot)

extent_plot <- ggplot(recovery_df %>% filter(calc == "extent"), aes(x = site_full, y = value)) +
  geom_col(aes(fill = treatment), position = "dodge") +
  scale_fill_manual(values = c(annual_col, continual_col)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 2.5)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  theme_bw() +
  labs(x = "Site", y = "Extent of recovery (mean kelp biomass) \n rise/\u0394",
       title = "Extent of recovery following experiment end") +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        title = element_text(size = 18),
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 16))
extent_plot
# ggsave(here::here("figures/recovery-metrics", paste("extent_", todays_date, ".jpg", sep = "")), extent_plot)

rate_plot <- ggplot(recovery_df %>% filter(calc == "rate"), aes(x = site_full, y = value)) +
  geom_col(aes(fill = treatment), position = "dodge") +
  scale_fill_manual(values = c(annual_col, continual_col)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 40)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  theme_bw() +
  labs(x = "Site", y = "Rate of recovery (mean kelp biomass between 'during' and 'after') \n rise/impact",
       title = "Rate of recovery following experiment end") +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 16),
        title = element_text(size = 18),
        legend.title = element_text(size = 16),
        legend.text = element_text(size = 16))
rate_plot
# ggsave(here::here("figures/recovery-metrics", paste("rate_", todays_date, ".jpg", sep = "")), rate_plot)
```

## Start-end-after

Look at average deltas across 3 years at start of experiment, 3 years at end of experiment, and 3 most recent years after experiment ended. Took out the first sampling dates in the set up script.  

Using `delta_annual` and `delta_continual` data frames. As a reminder:

```{r}
delta_annual_plot <- ggplot(delta_annual, aes(x = time_since_end, y = delta_annual)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(aes(col = exp_dates)) +
  geom_smooth(method = "lm", aes(col = exp_dates)) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 annual") +
  facet_wrap(~site_full, ncol = 1, scales = "free_y")

delta_continual_plot <- ggplot(delta_continual, aes(x = time_since_end, y = delta_continual)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(aes(col = exp_dates)) +
  geom_smooth(method = "lm", aes(col = exp_dates)) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 continual") +
  facet_wrap(~site_full, ncol = 1, scales = "free_y")

delta_annual_plot
delta_continual_plot
```


## Start-during-after
Which "kelp years" to pull out depends on the site because the experiment ended at different times. Fuck!

```{r}
##### all sites #####
# analysis of variance
annual_comp_2yrs_aov <- aov(delta_annual ~ comp_2yrs, data = delta_annual)

# summary
summary(annual_comp_2yrs_aov)

# Tukey and compact letter display
annual_comp_2yrs_tukey <- TukeyHSD(aov(delta_annual ~ comp_2yrs, data = delta_annual))
annual_comp_2yrs_cld <- multcompLetters4(annual_comp_2yrs_aov, annual_comp_2yrs_tukey)
annual_comp_2yrs_df <- enframe(annual_comp_2yrs_cld[[1]]$Letters)

##### AQUE #####
# analysis of variance
annual_aque_comp_2yrs_aov <- aov(delta_annual ~ comp_2yrs, data = (delta_annual %>% filter(site == "aque")))

# summary
summary(annual_aque_comp_2yrs_aov)

# Tukey and compact letter display
annual_aque_comp_2yrs_tukey <- TukeyHSD(annual_aque_comp_2yrs_aov)
annual_aque_comp_2yrs_cld <- multcompLetters4(annual_aque_comp_2yrs_aov, annual_aque_comp_2yrs_tukey)
annual_aque_comp_2yrs_df <- enframe(annual_aque_comp_2yrs_cld[[1]]$Letters)

##### NAPL #####
# analysis of variance
annual_napl_comp_2yrs_aov <- aov(delta_annual ~ comp_2yrs, data = (delta_annual %>% filter(site == "napl")))

# summary
summary(annual_napl_comp_2yrs_aov)

# Tukey and compact letter display
annual_napl_comp_2yrs_tukey <- TukeyHSD(annual_napl_comp_2yrs_aov)
annual_napl_comp_2yrs_cld <- multcompLetters4(annual_napl_comp_2yrs_aov, annual_napl_comp_2yrs_tukey)
annual_napl_comp_2yrs_df <- enframe(annual_napl_comp_2yrs_cld[[1]]$Letters)

##### IVEE #####
# analysis of variance
annual_ivee_comp_2yrs_aov <- aov(delta_annual ~ comp_2yrs, data = (delta_annual %>% filter(site == "ivee")))

# summary
summary(annual_ivee_comp_2yrs_aov)

# Tukey and compact letter display
annual_ivee_comp_2yrs_tukey <- TukeyHSD(annual_ivee_comp_2yrs_aov)
annual_ivee_comp_2yrs_cld <- multcompLetters4(annual_ivee_comp_2yrs_aov, annual_ivee_comp_2yrs_tukey)
annual_ivee_comp_2yrs_df <- enframe(annual_ivee_comp_2yrs_cld[[1]]$Letters)

##### MOHK #####
# analysis of variance
annual_mohk_comp_2yrs_aov <- aov(delta_annual ~ comp_2yrs, data = (delta_annual %>% filter(site == "mohk")))

# summary
summary(annual_mohk_comp_2yrs_aov)

# Tukey and compact letter display
annual_mohk_comp_2yrs_tukey <- TukeyHSD(annual_mohk_comp_2yrs_aov)
annual_mohk_comp_2yrs_cld <- multcompLetters4(annual_mohk_comp_2yrs_aov, annual_mohk_comp_2yrs_tukey)
annual_mohk_comp_2yrs_df <- enframe(annual_mohk_comp_2yrs_cld[[1]]$Letters)

##### CARP #####
# analysis of variance
annual_carp_comp_2yrs_aov <- aov(delta_annual ~ comp_2yrs, data = (delta_annual %>% filter(site == "carp")))

# summary
summary(annual_carp_comp_2yrs_aov)

# Tukey and compact letter display
annual_carp_comp_2yrs_tukey <- TukeyHSD(annual_carp_comp_2yrs_aov)
annual_carp_comp_2yrs_cld <- multcompLetters4(annual_carp_comp_2yrs_aov, annual_carp_comp_2yrs_tukey)
annual_carp_comp_2yrs_df <- enframe(annual_carp_comp_2yrs_cld[[1]]$Letters)


ggplot(delta_annual %>% drop_na(comp_2yrs), aes(x = comp_2yrs, y = delta_annual)) +
  geom_hline(yintercept = 0, lty = 2, alpha = 0.3) +
  geom_jitter(width = 0.2, alpha = 0.4) +
  stat_summary(aes(group = site), fun = mean, geom = "line") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  stat_summary(aes(col = site), fun = mean, geom = "point", size = 6) +
  scale_color_manual(values = site_palette) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time period", y = "\U0394 biomass (treatment - control)",
       title = "Annual removal, 2 year comparison") +
  facet_wrap(~site_full)




ggplot(delta_annual %>% drop_na(comp_3yrs), aes(x = comp_3yrs, y = delta_annual)) +
  geom_hline(yintercept = 0, lty = 2, alpha = 0.3) +
  geom_jitter(width = 0.2, alpha = 0.4) +
  stat_summary(aes(group = site), fun = mean, geom = "line") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  stat_summary(aes(col = site), fun = mean, geom = "point", size = 6) +
  scale_color_manual(values = site_palette) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time period", y = "\U0394 biomass (treatment - control)",
       title = "Annual removal, 3 year comparison") +
  facet_wrap(~site_full)

summary(aov(delta_annual ~ comp_3yrs, data = delta_annual))
TukeyHSD(aov(delta_annual ~ comp_3yrs, data = delta_annual))

summary(aov(delta_annual ~ comp_3yrs, data = (delta_annual %>% filter(site == "aque"))))
TukeyHSD(aov(delta_annual ~ comp_3yrs, data = (delta_annual %>% filter(site == "aque"))))

summary(aov(delta_annual ~ comp_3yrs, data = (delta_annual %>% filter(site == "napl"))))
TukeyHSD(aov(delta_annual ~ comp_3yrs, data = (delta_annual %>% filter(site == "napl"))))

summary(aov(delta_annual ~ comp_3yrs, data = (delta_annual %>% filter(site == "ivee"))))
TukeyHSD(aov(delta_annual ~ comp_3yrs, data = (delta_annual %>% filter(site == "ivee"))))

summary(aov(delta_annual ~ comp_3yrs, data = (delta_annual %>% filter(site == "mohk"))))
TukeyHSD(aov(delta_annual ~ comp_3yrs, data = (delta_annual %>% filter(site == "mohk"))))

summary(aov(delta_annual ~ comp_3yrs, data = (delta_annual %>% filter(site == "carp"))))
TukeyHSD(aov(delta_annual ~ comp_3yrs, data = (delta_annual %>% filter(site == "carp"))))

```


And for continual:
```{r}
ggplot(delta_continual %>% drop_na(comp_2yrs), aes(x = comp_2yrs, y = delta_continual)) +
  geom_hline(yintercept = 0, lty = 2, alpha = 0.3) +
  geom_jitter(width = 0.2, alpha = 0.4) +
  stat_summary(aes(group = site), fun = mean, geom = "line") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  stat_summary(aes(col = site), fun = mean, geom = "point", size = 6) +
  scale_color_manual(values = site_palette) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time period", y = "\U0394 biomass (treatment - control)",
       title = "continual removal, 2 year comparison") +
  facet_wrap(~site_full)

summary(aov(delta_continual ~ comp_2yrs, data = delta_continual))
TukeyHSD(aov(delta_continual ~ comp_2yrs, data = delta_continual))

summary(aov(delta_continual ~ comp_2yrs, data = (delta_continual %>% filter(site == "aque"))))
TukeyHSD(aov(delta_continual ~ comp_2yrs, data = (delta_continual %>% filter(site == "aque"))))

summary(aov(delta_continual ~ comp_2yrs, data = (delta_continual %>% filter(site == "napl"))))
TukeyHSD(aov(delta_continual ~ comp_2yrs, data = (delta_continual %>% filter(site == "napl"))))

summary(aov(delta_continual ~ comp_2yrs, data = (delta_continual %>% filter(site == "mohk"))))
TukeyHSD(aov(delta_continual ~ comp_2yrs, data = (delta_continual %>% filter(site == "mohk"))))

summary(aov(delta_continual ~ comp_2yrs, data = (delta_continual %>% filter(site == "carp"))))
TukeyHSD(aov(delta_continual ~ comp_2yrs, data = (delta_continual %>% filter(site == "carp"))))


ggplot(delta_continual %>% drop_na(comp_3yrs), aes(x = comp_3yrs, y = delta_continual)) +
  geom_hline(yintercept = 0, lty = 2, alpha = 0.3) +
  geom_jitter(width = 0.2, alpha = 0.4) +
  stat_summary(aes(group = site), fun = mean, geom = "line") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  stat_summary(aes(col = site), fun = mean, geom = "point", size = 6) +
  scale_color_manual(values = site_palette) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time period", y = "\U0394 biomass (treatment - control)",
       title = "continual removal, 3 year comparison") +
  facet_wrap(~site_full)

summary(aov(delta_continual ~ comp_3yrs, data = delta_continual))
TukeyHSD(aov(delta_continual ~ comp_3yrs, data = delta_continual))

summary(aov(delta_continual ~ comp_3yrs, data = (delta_continual %>% filter(site == "aque"))))
TukeyHSD(aov(delta_continual ~ comp_3yrs, data = (delta_continual %>% filter(site == "aque"))))

summary(aov(delta_continual ~ comp_3yrs, data = (delta_continual %>% filter(site == "napl"))))
TukeyHSD(aov(delta_continual ~ comp_3yrs, data = (delta_continual %>% filter(site == "napl"))))

summary(aov(delta_continual ~ comp_3yrs, data = (delta_continual %>% filter(site == "mohk"))))
TukeyHSD(aov(delta_continual ~ comp_3yrs, data = (delta_continual %>% filter(site == "mohk"))))

summary(aov(delta_continual ~ comp_3yrs, data = (delta_continual %>% filter(site == "carp"))))
TukeyHSD(aov(delta_continual ~ comp_3yrs, data = (delta_continual %>% filter(site == "carp"))))
```


```{r}
ggplot(delta_annual, aes(x = quarter, y = annual)) +
  geom_point(aes(group = kelp_year, col = kelp_year)) +
  geom_line(aes(group = kelp_year, col = kelp_year)) +
  facet_wrap(~site)
  
```


## linear model for recovery period

#### annual with seasonal data
```{r}
annual_after <- delta_annual %>% 
  filter(exp_dates == "after")
linear_model <- lm(delta_annual ~ time_since_end + site + time_since_end*site, data = annual_after, na.action = na.pass)
dredge(linear_model) %>% 
  model.sel() %>% 
  gt()

linear_model_sel <- lme(delta_annual ~ time_since_end, random = ~ 1|site, data = delta_annual %>% filter(exp_dates == "after"), na.action = na.pass)
summary(linear_model_sel)
linear_model_sel %>% 
  tbl_regression(intercept = TRUE) %>% 
  bold_p(t = 0.05)

linear_model_sel <- lmer(delta_annual ~ time_since_end + (1|site), data = annual_after, na.action = na.pass)
plot(simulateResiduals(linear_model_sel))
linear_model_during_seasonal <- lmer(delta_annual ~ time_since_end + (1|site), data = delta_annual %>% filter(exp_dates == "during"), na.action = na.pass)
summary(linear_model_during_seasonal)
plot(simulateResiduals(linear_model_during_seasonal))


# ggeffects
predicted <- ggpredict(linear_model_sel, terms = ~ time_since_end)
predicted_during <- ggpredict(linear_model_during_seasonal, terms = ~ time_since_end)
# emmeans
grid <- ref_grid(linear_model_sel, cov.keep = c("time_since_end"))
emm <- emmeans(grid, spec = c("time_since_end"), level = 0.95) %>% 
  data.frame(.)

ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  # facet_wrap(~fct_relevel(site_full, "Arroyo Quemado (AQUE)", "Naples (NAPL)", "Isla Vista (IVEE)", "Mohawk (MOHK)", "Carpinteria (CARP)"), ncol = 1, scales = "free_y") +
  geom_point(data = delta_annual, aes(x = time_since_end, y = delta_annual, color = exp_dates, shape = site)) +
  scale_color_manual(values = c("during" = "grey", "after" = "black"), guide = "none") +
  # during
  geom_ribbon(data = predicted_during, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), alpha = 0.5) +
  geom_line(data = predicted_during, aes(x = x, y = predicted)) +
  # after
  geom_ribbon(data = predicted, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), alpha = 0.5) +
  geom_line(data = predicted, aes(x = x, y = predicted)) +
  scale_x_continuous(breaks = seq(-11, 5, by = 1), minor_breaks = NULL) +
  scale_y_continuous(breaks = seq(-1500, 1500, by = 500)) +
  theme_bw() + 
  theme(axis.title = element_text(size = 16),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 14),
        legend.position = c(0.94, .18)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "Kelp (annual removal)", caption = "ggpredict")

ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  # facet_wrap(~fct_relevel(site_full, "Arroyo Quemado (AQUE)", "Naples (NAPL)", "Isla Vista (IVEE)", "Mohawk (MOHK)", "Carpinteria (CARP)"), ncol = 1, scales = "free_y") +
  geom_point(data = delta_annual, aes(x = time_since_end, y = delta_annual, color = exp_dates)) +
  scale_color_manual(values = c("during" = "grey", "after" = "black"), guide = "none") +
  geom_ribbon(data = emm, aes(x = time_since_end, y = emmean, ymin = lower.CL, ymax = upper.CL), alpha = 0.5) +
  geom_line(data = emm, aes(x = time_since_end, y = emmean)) + 
  theme_bw() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 annual", caption = "emmeans")
```

#### annual with "annualized" data

```{r}
annual_means <- delta_annual %>% 
  group_by(site, kelp_year) %>% 
  mutate(mean_delta = mean(delta_annual), 
         mean_tse = mean(time_since_end),
         se_delta = se(delta_annual)) %>% 
  dplyr::select(site, site_full, kelp_year, mean_delta, mean_tse, exp_dates, se_delta) %>% 
  unique() %>% 
  full_join(., site_quality, by = "site")

annual_after_means <- annual_means %>% 
  filter(exp_dates == "after")

linear_model <- lmer(mean_delta ~ mean_tse + (1|site), data = annual_after_means, na.action = na.pass)
linear_model2 <- lm(mean_delta ~ mean_tse, data = annual_after_means)
dredge(linear_model) %>% 
  model.sel() %>% 
  gt()
linear_model_sel <- lmer(mean_delta ~ mean_tse + (1|site), data = annual_after_means, na.action = na.pass)
summary(lme(mean_delta ~ mean_tse, random = ~ 1|site, data = annual_means %>% filter(exp_dates == "after")))
linear_model_during <- lmer(mean_delta ~ mean_tse + (1|site), data = annual_means %>% filter(exp_dates == "during"))
summary(linear_model_during)
summary(linear_model_sel)
plot(simulateResiduals(linear_model_sel))
check_model(linear_model_sel)
# ggeffects
predicted <- ggpredict(linear_model_sel, terms = ~ mean_tse + (1|site), type = "random") %>% 
  rename("site" = group) %>% 
  left_join(., enframe(sites_full), by = c("site" = "name")) %>% 
  rename("site_full" = value)
  # rename("site" = group) %>% 
  # left_join(., enframe(sites_full), by = c("site" = "name")) %>% 
  # rename("site_full" = value)

predicted_during <- ggpredict(linear_model_during, terms = ~ mean_tse + (1|site), type = "random") %>% 
  rename("site" = group) %>% 
  left_join(., enframe(sites_full), by = c("site" = "name")) %>% 
  rename("site_full" = value)
# emmeans
grid <- ref_grid(linear_model_sel, cov.keep = c("mean_tse"))
emm <- emmeans(grid, spec = c("mean_tse"), level = 0.95) %>% 
  data.frame(.) 

ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  # facet_wrap(~fct_relevel(site_full, "Arroyo Quemado (AQUE)", "Naples (NAPL)", "Isla Vista (IVEE)", "Mohawk (MOHK)", "Carpinteria (CARP)"), ncol = 1, scales = "free_y") +
  # raw data: means and error bars
  geom_point(data = annual_means, aes(x = mean_tse, y = mean_delta, shape = site), size = 2) +
  geom_errorbar(data = annual_means, aes(x = mean_tse, y = mean_delta, ymin = mean_delta - se_delta, ymax = mean_delta + se_delta)) +
  # geom_smooth(data = annual_means, aes(x = mean_tse, y = mean_delta, color = exp_dates), method = "lm") +
  geom_ribbon(data = predicted_during, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, fill = site), alpha = 0.5) +
  geom_line(data = predicted_during, aes(x = x, y = predicted, color = site)) +
  # predicted values: after period
  geom_ribbon(data = predicted, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, fill = site), alpha = 0.5) +
  geom_line(data = predicted, aes(x = x, y = predicted, color = site)) +
  # theme
  theme_bw() + 
  theme(legend.position = c(0.94, .18),
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 annual - annualized data", caption = "ggpredict")

ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  # facet_wrap(~fct_relevel(site_full, "Arroyo Quemado (AQUE)", "Naples (NAPL)", "Isla Vista (IVEE)", "Mohawk (MOHK)", "Carpinteria (CARP)"), ncol = 1, scales = "free_y") +
  geom_point(data = annual_means, aes(x = mean_tse, y = mean_delta, color = exp_dates, shape = site)) +
  geom_errorbar(data = annual_means, aes(x = mean_tse, y = mean_delta, ymin = mean_delta - se_delta, ymax = mean_delta + se_delta, color = exp_dates)) +
  scale_color_manual(values = c("during" = "grey", "after" = "black"), guide = "none") +
  scale_color_manual(values = c("during" = "grey", "after" = "black"), guide = "none") +
  geom_ribbon(data = emm, aes(x = mean_tse, y = emmean, ymin = lower.CL, ymax = upper.CL), alpha = 0.5) +
  geom_line(data = emm, aes(x = mean_tse, y = emmean)) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 annual - annualized data", 
       caption = "emmeans")
```

#### annual with "annualized" data for site quality
```{r}
annual_means <- delta_annual %>% 
  group_by(site, kelp_year) %>% 
  mutate(mean_delta = mean(delta_annual), 
         mean_tse = mean(time_since_end),
         se_delta = se(delta_annual)) %>% 
  dplyr::select(site, site_full, kelp_year, mean_delta, mean_tse, exp_dates, se_delta) %>% 
  unique() %>% 
  full_join(., site_quality, by = "site")

annual_after_means <- annual_means %>% 
  filter(exp_dates == "after")

linear_model <- lm(mean_delta ~ mean_tse + quality + mean_tse*quality, data = annual_after_means, na.action = na.pass)
dredge(linear_model) %>% 
  model.sel() %>% 
  gt()
linear_model_sel <- lm(mean_delta ~ mean_tse + quality + mean_tse*quality, data = annual_after_means, na.action = na.pass)
summary(linear_model_sel)
plot(simulateResiduals(linear_model_sel))
# ggeffects
predicted <- ggpredict(linear_model_sel, terms = ~ mean_tse + quality + mean_tse*quality, type = "fixed") %>% 
  rename("quality" = group) 
# emmeans
grid <- ref_grid(linear_model_sel, cov.keep = c("mean_tse", "quality"))
emm <- emmeans(grid, spec = c("mean_tse", "quality"), level = 0.95) %>% 
  data.frame(.)

annual_kelp_sitequality_ggpredict <- ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  # raw data: means and error bars
  facet_wrap(~quality, nrow = 1) +
  geom_point(data = annual_means, aes(x = mean_tse, y = mean_delta, color = exp_dates, shape = site)) +
  # geom_errorbar(data = annual_means, aes(x = mean_tse, y = mean_delta, ymin = mean_delta - se_delta, ymax = mean_delta + se_delta, color = exp_dates)) +
  scale_color_manual(values = c("during" = "grey", "after" = "black"), guide = "none") +
  # predicted values
  geom_ribbon(data = predicted, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, fill = quality), alpha = 0.5, show.legend = FALSE) +
  geom_line(data = predicted, aes(x = x, y = predicted)) +
  # theme
  theme_bw() + 
  theme(axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "Kelp biomass", caption = "ggpredict")

annual_kelp_sitequality_emmeans <-ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  facet_wrap(~quality, nrow = 1) +
  geom_point(data = annual_means, aes(x = mean_tse, y = mean_delta, color = exp_dates, shape = site)) +
  scale_color_manual(values = c("during" = "grey", "after" = "black"), guide = "none") +
  geom_ribbon(data = emm, aes(x = mean_tse, y = emmean, ymin = lower.CL, ymax = upper.CL, fill = quality), alpha = 0.5, show.legend = FALSE) +
  geom_line(data = emm, aes(x = mean_tse, y = emmean, col = quality)) +
  theme_bw() + 
  theme(axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 annual - annualized data", 
       caption = "emmeans")
```

#### annual with "annualized" data for the section

```{r}
annual_means_section <- delta_annual_section %>% 
  group_by(site, quad, side, kelp_year) %>% 
  mutate(mean_delta = mean(delta_annual), 
         mean_tse = mean(time_since_end),
         se_delta = se(delta_annual)) %>% 
  dplyr::select(site, site_full, quad, side, kelp_year, mean_delta, mean_tse, exp_dates, se_delta) %>% 
  unique() %>% 
  unite(quad_side, "quad", "side", remove = FALSE) %>% 
  full_join(., site_quality, by = "site")

annual_after_means_section <- annual_means_section %>% 
  filter(exp_dates == "after")

linear_model_section <- lmer(mean_delta ~ mean_tse + site + mean_tse*site + (1|quad_side), data = annual_after_means_section, na.action = na.pass)
dredge(linear_model_section) %>% 
  model.sel() %>% 
  gt()
linear_model_sel_section <- lmer(mean_delta ~ mean_tse + site + mean_tse*site + (1|quad_side), data = annual_after_means_section, na.action = na.pass)
summary(linear_model_sel_section)
plot(simulateResiduals(linear_model_sel_section))
# ggeffects
predicted_section <- ggpredict(linear_model_sel_section, terms = ~ mean_tse + site, type = "fixed") %>% 
  rename("site" = group) %>% 
  left_join(., enframe(sites_full), by = c("site" = "name")) %>% 
  rename("site_full" = value)
# emmeans
grid_section <- ref_grid(linear_model_sel_section, cov.keep = c("mean_tse", "site"))
emm_section <- emmeans(grid_section, spec = c("mean_tse", "site"), level = 0.95) %>% 
  data.frame(.) %>%
  left_join(., enframe(sites_full), by = c("site" = "name")) %>% 
  rename("site_full" = value)

ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  # facet_wrap(~fct_relevel(site_full, "Arroyo Quemado (AQUE)", "Naples (NAPL)", "Isla Vista (IVEE)", "Mohawk (MOHK)", "Carpinteria (CARP)"), ncol = 1) +
  # raw data: means and error bars
  geom_point(data = annual_means_section, aes(x = mean_tse, y = mean_delta, color = exp_dates)) +
  geom_smooth(data = annual_means_section, aes(x = mean_tse, y = mean_delta, aes(color = exp_dates)))
  geom_errorbar(data = annual_means_section, aes(x = mean_tse, y = mean_delta, ymin = mean_delta - se_delta, ymax = mean_delta + se_delta, color = exp_dates)) +
  scale_color_manual(values = c("during" = "grey", "after" = "black"), guide = "none") +
  # predicted values
  geom_ribbon(data = predicted_section, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, fill = site), alpha = 0.5) +
  geom_line(data = predicted_section, aes(x = x, y = predicted)) +
  # theme
  theme_bw() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 annual - annualized data", caption = "ggpredict")

ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  facet_wrap(~fct_relevel(site_full, "Arroyo Quemado (AQUE)", "Naples (NAPL)", "Isla Vista (IVEE)", "Mohawk (MOHK)", "Carpinteria (CARP)"), ncol = 1, scales = "free_y") +
  geom_point(data = annual_means_section, aes(x = mean_tse, y = mean_delta, color = exp_dates)) +
  scale_color_manual(values = c("during" = "grey", "after" = "black"), guide = "none") +
  geom_ribbon(data = emm_section, aes(x = mean_tse, y = emmean, ymin = lower.CL, ymax = upper.CL, fill = site), alpha = 0.5) +
  geom_line(data = emm_section, aes(x = mean_tse, y = emmean, col = site)) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 annual - annualized data", 
       subtitle = "transect section", 
       caption = "emmeans")

### site quality by section
linear_model_section <- lmer(mean_delta ~ mean_tse + quality + mean_tse*quality + (1|quad_side), data = annual_after_means_section, na.action = na.pass)
dredge(linear_model_section) %>% 
  model.sel() %>% 
  gt()
linear_model_sel_section <- lmer(mean_delta ~ mean_tse + quality + mean_tse*quality + (1|quad_side), data = annual_after_means_section, na.action = na.pass)
summary(linear_model_sel_section)
plot(simulateResiduals(linear_model_sel_section))
# ggeffects
predicted_section <- ggpredict(linear_model_sel_section, terms = ~ mean_tse + quality + mean_tse*quality, type = "fixed") %>% 
  rename("quality" = group) 
# emmeans
grid_section <- ref_grid(linear_model_sel_section, cov.keep = c("mean_tse", "quality"))
emm_section <- emmeans(grid_section, spec = c("mean_tse", "quality"), level = 0.95) %>% 
  data.frame(.) 

ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  facet_wrap(~quality, nrow = 1) +
  # raw data: means and error bars
  geom_point(data = annual_means_section, aes(x = mean_tse, y = mean_delta, color = exp_dates)) +
  geom_errorbar(data = annual_means_section, aes(x = mean_tse, y = mean_delta, ymin = mean_delta - se_delta, ymax = mean_delta + se_delta, color = exp_dates)) +
  scale_color_manual(values = c("during" = "grey", "after" = "black"), guide = "none") +
  # predicted values
  geom_ribbon(data = predicted_section, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, fill = quality), alpha = 0.5) +
  geom_line(data = predicted_section, aes(x = x, y = predicted)) +
  # theme
  theme_bw() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 annual - annualized data", caption = "ggpredict")

ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  facet_wrap(~ quality, ncol = 1) +
  geom_point(data = annual_means_section, aes(x = mean_tse, y = mean_delta, color = exp_dates)) +
  scale_color_manual(values = c("during" = "grey", "after" = "black"), guide = "none") +
  geom_ribbon(data = emm_section, aes(x = mean_tse, y = emmean, ymin = lower.CL, ymax = upper.CL, fill = quality), alpha = 0.5) +
  geom_line(data = emm_section, aes(x = mean_tse, y = emmean, col = quality)) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 10),
        strip.text = element_text(size = 10)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)",
       title = "\U0394 annual - annualized data", 
       subtitle = "transect section", 
       caption = "emmeans")
```

#### continual with site only
```{r}
continual_after <- delta_continual %>% 
  filter(exp_dates == "after")

linear_model_kelp_lme <- lme(delta_continual ~ time_since_end, random = ~ 1|time_since_end/site, 
                        data = continual_after, na.action = na.pass)
summary(linear_model_kelp_lme)
plot(simulateResiduals(linear_model_kelp_lme))

linear_model_kelp_lmer <- lmer(delta_continual ~ time_since_end + (1 + time_since_end|site), 
                         data = continual_after, na.action = na.pass)
plot(simulateResiduals(linear_model_kelp_lmer))
check_model(linear_model_kelp_lmer)

linear_model_kelp_lme %>% 
  tbl_regression() %>% 
  bold_p(t = 0.05)

AICc(linear_model_kelp_lme, linear_model_kelp_lmer)

linear_model_kelp_during_lme <- lme(delta_continual ~ time_since_end, 
                                    random = ~ 1|time_since_end/site, 
                                    data = delta_continual)
summary(linear_model_kelp_during_lme)

linear_model_kelp_during_lmer <- lmer(delta_continual ~ time_since_end + (1 + time_since_end|site), 
                                     data = delta_continual %>% filter(exp_dates == "during"), na.action = na.pass)
plot(simulateResiduals(linear_model_kelp_during_lmer))
linear_model_during_seasonal_v2 <- lmer(delta_continual ~ time_since_end + (1 + time_since_end|site),
                                     data = delta_continual %>% filter(exp_dates == "during"), na.action = na.pass)
AICc(linear_model_kelp_during_lmer, linear_model_during_seasonal_v2)
# AICc(linear_model_during_seasonal, linear_model_during_seasonal_v2)


# ggeffects
# after
predicted_kelp_after_overall <- ggpredict(linear_model_kelp_lmer, terms = ~ time_since_end, type = "fixed")
predicted_kelp_after_aque <- ggpredict(linear_model_kelp_lmer, terms = ~ time_since_end, type = "random", condition = c(site = "aque"))
predicted_kelp_after_napl <- ggpredict(linear_model_kelp_lmer, terms = ~ time_since_end, type = "random", condition = c(site = "napl"))
predicted_kelp_after_mohk <- ggpredict(linear_model_kelp_lmer, terms = ~ time_since_end, type = "random", condition = c(site = "mohk"))
predicted_kelp_after_carp <- ggpredict(linear_model_kelp_lmer, terms = ~ time_since_end, type = "random", condition = c(site = "carp"))

# during
predicted_kelp_during_overall <- ggpredict(linear_model_kelp_during_lmer, terms = ~ time_since_end, type = "fixed")
predicted_kelp_during_aque <- ggpredict(linear_model_kelp_during_lmer, terms = ~ time_since_end, type = "random", condition = c(site = "aque"))
predicted_kelp_during_napl <- ggpredict(linear_model_kelp_during_lmer, terms = ~ time_since_end, type = "random", condition = c(site = "napl"))
predicted_kelp_during_mohk <- ggpredict(linear_model_kelp_during_lmer, terms = ~ time_since_end, type = "random", condition = c(site = "mohk"))
predicted_kelp_during_carp <- ggpredict(linear_model_kelp_during_lmer, terms = ~ time_since_end, type = "random", condition = c(site = "carp"))

overall <- ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(data = delta_continual, 
             aes(x = time_since_end, y = delta_continual, fill = site, shape = site), size = 3, alpha = 0.9) +
  scale_shape_manual(values = shape_palette_site) +
  scale_fill_manual(values = color_palette_site) +
  # new_scale("color") + 
  # overall
  geom_line(data = predicted_kelp_after_overall, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_after_overall, aes(x = x, ymax = conf.high, ymin = conf.low), alpha = 0.2) +
  geom_line(data = predicted_kelp_during_overall, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_during_overall, aes(x = x, ymax = conf.high, ymin = conf.low), alpha = 0.2) +
  scale_x_continuous(breaks = seq(-8, 5, by = 1), minor_breaks = NULL) +
  scale_y_continuous(breaks = seq(-1500, 1500, by = 1000), limits = c(-1800, 1500)) +
  theme_bw() + 
  theme(axis.title = element_text(size = 18),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 16), 
        legend.position = c(0.18, 0.87), 
        plot.margin = margin(0, 0, 0, 0)) +
  labs(x = "Time since end of removal", y = "\U0394 kelp biomass (treatment - control)")

aque <- ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(data = delta_continual %>% filter(site == "aque"), aes(x = time_since_end, y = delta_continual), shape = aque_shape, fill = aque_col, size = 3, alpha = 0.9) +
  # during
  geom_line(data = predicted_kelp_during_aque, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_during_aque, aes(x = x, ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  # after
  geom_line(data = predicted_kelp_after_aque, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_after_aque, aes(x = x, ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  scale_x_continuous(breaks = seq(-8, 5, by = 1), minor_breaks = NULL) +
  scale_y_continuous(breaks = seq(-1500, 1500, by = 1000), limits = c(-1800, 1500)) +
  geom_text(aes(x = -6.6, y = 1400), label = "aque", size = 8) +
  theme_bw() + 
  theme(axis.title = element_text(size = 18),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        legend.position = "none", 
        axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        plot.margin = margin(0, 0, 0, 0)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)")

napl <- ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(data = delta_continual %>% filter(site == "napl"), aes(x = time_since_end, y = delta_continual), shape = napl_shape, fill = napl_col, size = 3, alpha = 0.9) +
  # during
  geom_line(data = predicted_kelp_during_napl, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_during_napl, aes(x = x, ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  # after
  geom_line(data = predicted_kelp_after_napl, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_after_napl, aes(x = x, ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  scale_x_continuous(breaks = seq(-8, 5, by = 1), minor_breaks = NULL) +
  scale_y_continuous(breaks = seq(-1500, 1500, by = 1000), limits = c(-1800, 1500)) +
  geom_text(aes(x = -6.8, y = 1400), label = "napl", size = 8) +
  theme_bw() + 
  theme(axis.title = element_text(size = 18),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        plot.margin = margin(0, 0, 0, 0)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)")

mohk <- ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(data = delta_continual %>% filter(site == "mohk"), aes(x = time_since_end, y = delta_continual), shape = mohk_shape, fill = mohk_col, size = 3, alpha = 0.9) +
  # during
  geom_line(data = predicted_kelp_during_mohk, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_during_mohk, aes(x = x, ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  # after
  geom_line(data = predicted_kelp_after_mohk, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_after_mohk, aes(x = x, ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  scale_x_continuous(breaks = seq(-8, 5, by = 1), minor_breaks = NULL) +
  scale_y_continuous(breaks = seq(-1500, 1500, by = 1000), limits = c(-1800, 1500)) +
  geom_text(aes(x = -6.6, y = 1400), label = "mohk", size = 8) +
  theme_bw() + 
  theme(axis.title = element_text(size = 18),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        plot.margin = margin(0, 0, 0, 0)) +
  labs(x = "Time since end of experiment", y = "\U0394 biomass (treatment - control)")

carp <- ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(data = delta_continual %>% filter(site == "carp"), aes(x = time_since_end, y = delta_continual), shape = carp_shape, fill = carp_col, size = 3, alpha = 0.9) +
  # during
  geom_line(data = predicted_kelp_during_carp, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_during_carp, aes(x = x, ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  # after
  geom_line(data = predicted_kelp_after_carp, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_after_carp, aes(x = x, ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  scale_x_continuous(breaks = seq(-8, 5, by = 1), minor_breaks = NULL) +
  scale_y_continuous(breaks = seq(-1500, 1500, by = 1000), limits = c(-1800, 1500)) +
  geom_text(aes(x = -6.8, y = 1400), label = "carp", size = 8) +
  theme_bw() + 
  theme(axis.title = element_text(size = 18),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        legend.position = "none",
        axis.title.y = element_blank(),
        plot.margin = margin(0, 0, 0, 0)) +
  labs(x = "Time since end of removal", y = "\U0394 biomass (treatment - control)")

# y-axis label for patchwork side eye emoji
yaxislabel <- ggplot(data.frame(l = "\U0394 biomass (treatment - control)", x = 1, y = 1)) +
  geom_text(aes(x, y, label = l), angle = 90) + 
  theme_void() +
  theme(plot.margin = margin(0, 0, 0, 0)) +
  coord_cartesian(clip = "off")

plots_together <- overall + aque/napl/mohk/carp 
plots_together
# ggsave(here::here("figures", paste("delta_continual-", todays_date, ".jpg", sep = "")), plot = plots_together, height = 8, width = 16, dpi = 150)
```

### continual with site quality

```{r}
linear_model_kelp_lme <- lme(delta_continual ~ time_since_end + quality + time_since_end*quality, 
                        random = ~ 1|site, 
                        data = continual_after, na.action = na.pass)
summary(linear_model_kelp_lme)
linear_model_kelp_lme %>% 
  tbl_regression() %>% 
  bold_p(t = 0.05)

linear_model_kelp_lmer <- lmer(delta_continual ~ time_since_end + quality + time_since_end*quality + (1|site), 
                         data = continual_after, na.action = na.pass)
plot(simulateResiduals(linear_model_kelp_lmer))
summary(linear_model_kelp_lmer)

AICc(linear_model_kelp_lme, linear_model_kelp_lmer)


linear_model_kelp_during_lme <- lme(delta_continual ~ time_since_end + quality + time_since_end*quality, 
                                    random = ~ 1|site, 
                                    data = delta_continual %>% filter(exp_dates == "during"))
summary(linear_model_kelp_during_lme)

linear_model_kelp_during_lmer <- lmer(delta_continual ~ time_since_end + quality + time_since_end*quality + (1|site), 
                                     data = delta_continual %>% filter(exp_dates == "during"), na.action = na.pass)
plot(simulateResiduals(linear_model_kelp_during_lmer))
# linear_model_during_seasonal_v2 <- lmer(delta_continual ~ time_since_end + (1 + time_since_end|site), 
#                                      data = delta_continual %>% filter(exp_dates == "during"), na.action = na.pass)
# AICc(linear_model_during_seasonal, linear_model_during_seasonal_v2)


# ggeffects
# after
predicted_kelp_after_quality <- ggpredict(linear_model_kelp_lmer, terms = ~ time_since_end + quality + time_since_end*quality, type = "fixed") %>% 
  rename("quality" = group)
predicted_kelp_after_overall <- ggpredict(linear_model_kelp_lmer, terms = ~ time_since_end, type = "fixed")

# during
predicted_kelp_during_quality <- ggpredict(linear_model_kelp_during_lmer, terms = ~ time_since_end + quality + time_since_end*quality, type = "fixed") %>% 
  rename("quality" = group)
predicted_kelp_during_overall <- ggpredict(linear_model_kelp_during_lmer, terms = ~ time_since_end, type = "fixed")

overall <- ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(data = delta_continual, 
             aes(x = time_since_end, y = delta_continual, fill = site, shape = site), size = 3, alpha = 0.9) +
  scale_shape_manual(values = shape_palette_site) +
  scale_fill_manual(values = color_palette_site) +
  # new_scale("color") + 
  # overall
  geom_line(data = predicted_kelp_after_overall, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_after_overall, aes(x = x, ymax = conf.high, ymin = conf.low), alpha = 0.4) +
  geom_line(data = predicted_kelp_during_overall, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_during_overall, aes(x = x, ymax = conf.high, ymin = conf.low), alpha = 0.4) +
  scale_x_continuous(breaks = seq(-8, 5, by = 1), minor_breaks = NULL) +
  scale_y_continuous(breaks = seq(-1500, 1000, by = 1000), limits = c(-1800, 1000)) +
  theme_bw() + 
  theme(axis.title = element_text(size = 16),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 14),
        legend.text = element_text(size = 14), 
        legend.position = c(0.15, 0.87), 
        plot.margin = margin(0, 0, 0, 0)) +
  labs(x = "Time since end of experiment", y = "\U0394 kelp biomass (treatment - control)")

high <- ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(data = delta_continual %>% filter(quality == "high"), aes(x = time_since_end, y = delta_continual), shape = mohk_shape, fill = mohk_col, size = 3, alpha = 0.9) +
  # during
  geom_line(data = predicted_kelp_during_quality %>% filter(quality == "high"), aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_during_quality %>% filter(quality == "high"), aes(x = x, ymax = conf.high, ymin = conf.low), alpha = 0.5) +
  # after
  geom_line(data = predicted_kelp_after_quality %>% filter(quality == "high"), aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_after_quality %>% filter(quality == "high"), aes(x = x, ymax = conf.high, ymin = conf.low), alpha = 0.5) +
  scale_x_continuous(breaks = seq(-8, 5, by = 1), minor_breaks = NULL) +
  scale_y_continuous(breaks = seq(-1500, 1000, by = 1000), limits = c(-1800, 1000)) +
  geom_text(aes(x = -6.6, y = 1000), label = "high", size = 8) +
  theme_bw() + 
  theme(axis.title = element_text(size = 16),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 14),
        legend.text = element_text(size = 14), 
        legend.position = "none", 
        axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        plot.margin = margin(0, 0, 0, 0)) +
  labs(x = "Time since end of experiment", y = "\U0394 kelp biomass (treatment - control)")

medium <- ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(data = delta_continual %>% filter(quality == "medium"), aes(x = time_since_end, y = delta_continual, shape = site, fill = site), size = 3, alpha = 0.9) +
  scale_shape_manual(values = c("aque" = aque_shape, "napl" = napl_shape)) +
  scale_fill_manual(values = c("aque" = aque_col, "napl" = napl_col)) +
  # during
  geom_line(data = predicted_kelp_during_quality %>% filter(quality == "medium"), aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_during_quality %>% filter(quality == "medium"), aes(x = x, ymax = conf.high, ymin = conf.low), alpha = 0.5) +
  # after
  geom_line(data = predicted_kelp_after_quality %>% filter(quality == "medium"), aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_after_quality %>% filter(quality == "medium"), aes(x = x, ymax = conf.high, ymin = conf.low), alpha = 0.5) +
  scale_x_continuous(breaks = seq(-8, 5, by = 1), minor_breaks = NULL) +
  scale_y_continuous(breaks = seq(-1500, 1000, by = 1000), limits = c(-1800, 1000)) +
  geom_text(aes(x = -6.6, y = 1000), label = "medium", size = 8) +
  theme_bw() + 
  theme(axis.title = element_text(size = 16),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 14),
        legend.text = element_text(size = 14), 
        legend.position = "none", 
        axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        plot.margin = margin(0, 0, 0, 0)) +
  labs(x = "Time since end of experiment", y = "\U0394 kelp biomass (treatment - control)")

low <- ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(data = delta_continual %>% filter(quality == "low"), aes(x = time_since_end, y = delta_continual), shape = carp_shape, fill = carp_col, size = 3, alpha = 0.9) +
  # during
  geom_line(data = predicted_kelp_during_quality %>% filter(quality == "low"), aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_during_quality %>% filter(quality == "low"), aes(x = x, ymax = conf.high, ymin = conf.low), alpha = 0.5) +
  # after
  geom_line(data = predicted_kelp_after_quality %>% filter(quality == "low"), aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_after_quality %>% filter(quality == "low"), aes(x = x, ymax = conf.high, ymin = conf.low), alpha = 0.5) +
  scale_x_continuous(breaks = seq(-8, 5, by = 1), minor_breaks = NULL) +
  scale_y_continuous(breaks = seq(-1500, 1000, by = 1000), limits = c(-1800, 1000)) +
  geom_text(aes(x = -6.6, y = 900), label = "low", size = 8) +
  theme_bw() + 
  theme(axis.title = element_text(size = 16),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 14),
        legend.text = element_text(size = 14), 
        legend.position = "none", 
        axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        plot.margin = margin(0, 0, 0, 0)) +
  labs(x = "Time since end of experiment", y = "\U0394 kelp biomass (treatment - control)")

plots_together <- overall + (high/medium/low)
plots_together
ggsave(here::here("figures", paste("delta_continual_quality-", todays_date, ".jpg", sep = "")), plot = plots_together, height = 8, width = 16, dpi = 150)
```


### continual (raw biomass)

```{r}
linear_model_kelp_raw_lme <- lme(continual ~ time_since_end, 
                        random = ~ 1|site, 
                        data = continual_after, na.action = na.pass)
summary(linear_model_kelp_raw_lme)

linear_model_kelp_raw_lmer <- lmer(continual ~ time_since_end + (1|site), 
                         data = continual_after, na.action = na.pass)

AICc(linear_model_kelp_raw_lme, linear_model_kelp_raw_lmer)
plot(simulateResiduals(linear_model_kelp_lmer))

linear_model_kelp_raw_during_lme <- lme(continual ~ time_since_end, 
                                    random = ~ 1|site, 
                                    data = delta_continual)
summary(linear_model_kelp_raw_during_lme)

linear_model_kelp_raw_during_lmer <- lmer(continual ~ time_since_end + (1|site), 
                                     data = delta_continual %>% filter(exp_dates == "during"), na.action = na.pass)
plot(simulateResiduals(linear_model_kelp_raw_during_lmer))

# after
predicted_kelp_raw_after_site <- ggpredict(linear_model_kelp_raw_lmer, terms = ~ time_since_end + (1|site), type = "random") %>% 
  rename("site" = group)
predicted_kelp_raw_after_overall <- ggpredict(linear_model_kelp_raw_lmer, terms = ~ time_since_end, type = "fixed")

# during
predicted_kelp_raw_during_site <- ggpredict(linear_model_kelp_raw_during_lmer, terms = ~ time_since_end + (1|site), type = "fixed") %>% 
  rename("site" = group)
predicted_kelp_raw_during_overall <- ggpredict(linear_model_kelp_raw_during_lmer, terms = ~ time_since_end, type = "fixed")

ggplot() +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(data = delta_continual,
             aes(x = time_since_end, y = control, shape = site), size = 3, alpha = 0.4) +
  geom_point(data = delta_continual, 
             aes(x = time_since_end, y = continual, fill = site, shape = site), size = 3, alpha = 0.9) +
  scale_shape_manual(values = shape_palette_site) +
  scale_fill_manual(values = color_palette_site) +
  # new_scale("color") + 
  # overall
  geom_line(data = predicted_kelp_raw_after_overall, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_raw_after_overall, aes(x = x, ymax = conf.high, ymin = conf.low), alpha = 0.4) +
  geom_line(data = predicted_kelp_raw_during_overall, aes(x = x, y = predicted), size = 2) +
  geom_ribbon(data = predicted_kelp_raw_during_overall, aes(x = x, ymax = conf.high, ymin = conf.low), alpha = 0.4) +
  scale_x_continuous(breaks = seq(-8, 5, by = 1), minor_breaks = NULL) +
  # scale_y_continuous(breaks = seq(-1500, 1500, by = 1000), limits = c(-1800, 1500)) +
  theme_bw() + 
  theme(axis.title = element_text(size = 16),
        plot.title = element_text(size = 18),
        axis.text = element_text(size = 14),
        legend.text = element_text(size = 14), 
        legend.position = c(0.15, 0.87), 
        plot.margin = margin(0, 0, 0, 0)) +
  labs(x = "Time since end of experiment", y = "Kelp biomass",
      caption = "high point is MOHK on 2019-11-19")
```

















